\section{Expected Encounter}

I was sitting in my throne chamber in silence as heavy minutes flew by one by one. It was quite excruciating to force myself to do absolutely nothing but waiting, knowing that my master plan is reaching its pinnacle. But then, impatient people never become the Dark Overlords, do they?

I knew it would come to this. I wanted it to. I dreamed of it. I carefully crafted every bit of every circumstance I could affect to make it happen this way. When the fate of several nations is at stake, no detail is minute.

The last rays of sunlight swept across the chamber ceiling and dusk began to settle. The door lock clanked at the edge of perception and shadowy silhouette appeared in the frame.

\say{My Lord,} said silhouette, \say{the Hero has been spotted at the Blacksmith suburbs just ten minutes ago.}

I pondered this information for some time. Frankly, I quit feeling surprised by the tactical decisions of the Heroes long ago, before this particular one was even born. But still!

There were three general approaches to the Dark Citadel. One could land ashore by boat and climb the rocky cliff to reach the least guarded Oceanwatch tower. Being mostly equipped to deal with naval threats the vantage points allowing the personnel to look directly down were rare and usually understaffed. Tough, but not impossible, especially at nighttime.

One could also take Merchant pathway and blend with townsfolk to reach the marketplace inside Outer Court of the Citadel and its numerous warehouses and cellars. Hundreds of suppliers go there and back every business day. With a bit of luck the potential intruder could navigate vast underground tunnel system to reach Inner Court and from there -- my chambers. But that, of course, will only work during the day, and our Hero seems to have preference for more dramatic background lighting conditions.

Finally, one can enter the main eastward gates of the city and take all the way through Blacksmith’s, a drawbridge across the Fast River, past the Temple of All Gods, a Rosemeadow households, another drawbridge across the same Fast River, past the army barracks, and end up at the gates to the Outer Court. Which are closed for night. With manned guard posts at every bridge and sentinel monks patrolling between drawbridges in the Temple district.

Despite my best efforts I never stop wondering how Hero’s brain worked in a situations like this. You have been presented with three options – one to use the best of your physique, one to show your innate mastery of stealth and secrecy and another one is to completely depend on your sheer luck, unwarranted self-importance and overinflated charisma. Which ones do they chose? Go figure. Ah, and they call it “leadership”.

The problem was that it worked so much more often than should have been logically expected, it made me wonder whether our universe is driven by the narrative rather than causality.

\say{Very good}, I replied. \say{Carry on.}

The silhouette vanished. Twenty more minutes flew by as I was seriously considering taking a short nap, but suddenly I felt the ground slightly shake and seconds after a distant rumble was clearly heard.

This was interesting. Either the attacking party had packed a bunch of explosives or they had a battle mage. If this noise was the breach of the front gates to the Outer Court, they were still too far away for me to feel the difference.

Some more minutes flew by. At the very edge of my perception I heard metal clanking noises and several loud cries of the battle.

I never underestimate my enemies no matter how stupid they are or try to appear. Too many Dark Overlords in the past fell victims to their own overconfidence. A little less many fell victims to their inability to comprehend that by virtue of unpredictability the ultimate stupidity is far more dangerous than an intelligence and knowledge put to a good use. Therefore you shall never constrain yourself in the expectations of the capabilities of your adversary.

Right\dots This all sounds very good in theory. But the practice of half a dozen or less people storming the guarded Dark Citadel in head-on assault is entirely different. Deep in my mind the genuine worry started to creep. You can never be 100\% sure, it whispered. The absolute categories do not belong to this world. There were some ways, no matter how improbable, for this warband to defeat me in a way I do not anticipate.

Another explosion shook the grounds and a thunder-like sound followed shortly after. I felt the prickling sensation in the back of my head. Yes, this was a battle mage. And a powerful one, it seems. The honorable guests have just breached the gates to the Inner Court.

\say{Exmer,} I called.

\say{Yes, my Lord?} The dark silhouette almost like condensed from the thin air by the door.

\say{That would be all for now, Exmer. Take a vacation, give the boys some rest.}

\say{Yes, my Lord. Thank you.}

Now an interesting part. The Inner Court takes about two minutes to cross in the jogging pace from the gates to the entrance of the sanctum. It will take at least five more minutes to ascend ten floors to reach the upper halls. And anywhere from one to ten minutes to figure out in which hall the back door leads to the throne chamber. Unless the guests had an ingenious idea of splitting up or had somehow secured a map of the upper level, it will take them anywhere from eight to seventeen minutes until they find me. During that specific timeframe, Citadel guards will not attack them, or even be there, for that matter. To expect them to come to the conclusion that I am not present in the chambers now is too far fetched, of course, but any at least slightly reasonable tactical-minded attacker would be immediately suspicious.

My original plan did not foresee the battle mage in the party at all. I should have just challenged the Hero to a hand-to-hand duel, invoking ancient rite of trial by combat, agreeing to not use any magic in the encounter. To a complete outsider the chances of sixty-something old gray-haired crook whose joints barely held together against much younger, stronger and motivated Hero at his peak physical capabilities were predetermined. But this was where the audience will be gravely surprised. In our world an individual seriously involved in warfare and power struggles will rarely live up to such an advanced age if he did not pack something surprising up his sleeve. Figuratively speaking. Especially figuratively speaking.

But then they somehow convinced the Priest to join the party. At first I thought it will be just another minor nuisance to deal with. But the more I considered the situation the more I realized how many of a much greater opportunities this sudden change presented for me. The Priest could and should provide the very legitimacy with which my master plan will be cemented.

I took this time to rethink the plan again and again, adding several probable scenarios to it given newly discovered circumstances. If I am lucky and battle mage is an experienced one, he will unlikely to engage in a direct confrontation with me but rather will try to understand what is going on and how to play along with it. But if it is someone who had just graduated from sentinel monks and been given his first tunic, then -- who knows. I am very reluctant to harm seriously the servants of the Temple, regardless of the rank. Bad omen, you know. I should have spent some efforts to investigate who he was and, more importantly, how exactly the Hero convinced him to join his cause. Not a big drawback actually, but still. It appears I spent too much time focusing on Hero's character, disregarding his aides and their potential.

Anyway, what else? I felt like my thoughts raced as runaway cart downhill. Surely, I can stop them from attacking me, that is easy, but I needed them to talk, and that is not so easy. Provided the legal issues could be settled by the authority of the Temple with some persuasion\dots The Hero. What are his benefits beyond obvious vengeance and recognition by domestic political establishment? And if none, could I just subtly offer him some? And what if he and my heir\dots Oh, shit\dots

And just a moment before the door to the throne chamber burst open, the last puzzle piece clicked into place and the lightning revelation struck me and I saw the great picture of all great pictures, froze in awe before the crystal clarity and sheer magnitude of \textit{what must be done}.

It took them ten minutes to find me and a few people with lit torches poured in and spread in a distinctive semicircular pattern along the walls opposite the throne.

\section{The Warband}

Unlike most of the hallways the throne chamber’s windows were high and close to the ceiling. The throne was traditionally situated opposite the entrance at the elevated dais and located so that rising sun will illuminate the sitting monarch giving the environment a taste of royal divinity. At other times, the chambers was meant to be lit either by torches or daylight. Neither was the case now, and if you enter the throne chamber from the much darker hallways the only things you can see at first are the windows, especially now that evening dusk was not yet over. And everything else, like the large tables to the side of the throne, were almost completely invisible especially if you hold a torch in your hand.

I quietly watched the party. The Hero was so archetypal it nearly made me smile. Moderately tall very muscular man in his mid-twenties with dark wavy hair descending on his shoulders, brown piercing eyes, extended jaw as though chiseled from stone, perfectly straight nose, head sitting on a neck just as thick, mandatory scar across the left cheek, arms with muscles as prominent he may just crush your skull easily if he wanted to and a ribcage so broad it make his torso appear triangular from that distance. The Hero wielded a two-handed sword and a torch.

Standing right next to him was much taller and skinnier man covered in leather armor and wearing fur hat, his branch-like limbs wielding an armed and cocked crossbow in a ready to shoot position.

To the other side of the Hero stood a man in a simple gray tunic, leather belt with numerous pockets and wearing sandals. He was completely bald, his wrists and palms were emitting barely visible reddish glow. The battle mage, as they are. My wild guess would be that this one was no less than a Cradle Priest. I felt a little bit of relief.

Finally, between the Hero and the mage stood yet another intruder not needing any introduction or analysis. My beloved Alice, my little girl, the warmth of my life, the only living being in this world in whom I truly found a genuine joy. My daughter.

Having just now lurked in the upper hallways none of them should have seen me sitting behind the table for at least half a minute. And yet everyone's gaze and one's crossbow was fixed dead straight on my humble outline. What was it? A magically enhanced eyesight? A good tactical training? Or was I sitting in the only place in the chamber with shadow big enough to hide in? Oh, crap, I'm getting old.

All right, since they see me anyway, it is time to introduce myself.

\say{Welcome, good lady and honorable gentlemen.} I waved my hand and torches across the throne chamber flashed and ignited. \say{Please, have your seats. You must be tired after your long and eventful journey here.}

The fur hat jumped in surprise and let one bolt loose. The mage clapped his hands and engulfed himself in a nearly invisible glow of the magic shield. The Hero jumped on a table and ran towards me screaming and waving his sword.

What were they actually hoping for?

Five seconds later the Hero was carefully touching the back of his head after it collided with a nearby wall with rather unexpected velocity. His sword cracked and broken in three pieces laid nearby on the floor. The fur hat was sitting on the floor stupidly looking at the snapped bowstring and a bolt split in two and visibly charred at the crack. The battle mage was nervously alternating his gaze between me and the entrance door right after it slammed shut in front of him apparently trying to run away. Alice was kneeling by the Hero, asking if he was hurt, hugging him and murmuring something caring and encouraging.

I cleared throat.

\say{All right, let us try this again. However, before we proceed, let it be known that I am genuinely offended by your disrespectful behavior and threatening attitude. With the exception of this good lady here, I have never seen any one of you in my life and, to my best knowledge, I have never done any of you or those dear to you any harm that would warrant your warband to burst into my home in such an unpleasant manner, let alone with the apparently homicidal intent.}

The party listened gloomily and quietly.

\say{So, please, take your seats and we will try to resolve our enmities in a civilized manner, shall we?}

The quartet cautiously sat at the far side of a table.

\say{As a good-mannered host I would have offered you a drink, but something tells me that your level of distrust at this moment might render this gesture unappreciated and useless. So, down to business. Who is in charge of your party?}

The Hero opened his mouth and took a breath but Alice suddenly interrupted:

\say{You cannot pretend I am not existing! You can not pretend you do not notice me!}

The Hero turned to her and put his hand over hers, nodding reassuringly.

\say{Other than these two statements are mutually contradictory,} I replied, \say{I can assure you that I, on the contrary, fully ascertain your existence and, moreover, I do notice you. That I do not react to these two aforementioned facts in the manner you rather expecting, is not \textit{my} fault, per se. But if it makes you feel any better, I am actually very glad to see you alive and well after all these years since you ran away from home and I am truly enjoying this fact. Happy now?}

Crooked grin appeared on Alice face and she opened her mouth to say something even more insulting but this time Hero just squeezed her hands in his firmly and she went quiet.

\say{My name is Ferin,} the Hero begun, \say{I come from the seafaring tribes of the Nation of Ezeek. Ezeek was once a rich, prosperous and glorious land and people of its tribes are widely known for hospitality and generosity as well as bravery of its fearless warriors. Our history goes and is remembered as many generations back, our legends and tales are retold worldwide. Ezeek tribesmen are respected across the continent and beyond.}

Aww, yeah. The good old nationalist resentment. You have never failed me.

\say{All of this is now history,} Ferin continued. \say{The Great Winter War devastated and depleted our lands, divided our tribes, turned brother against brother and son against father. Almost one third of our fertile lands have been taken from us. We no longer command respect, we are being laughed and spat upon. Our nation is declining, less and less people want to take Ezeek women as wives, and many youth are fleeing the land never to return, our children no longer remember their true ancestry, our elders die alone in neglect.}

\say{I have got the overall picture, Ferin,} I mused. \say{Make your point.}

\say{I am the youngest son of Prince Enceris. I am the only surviving member of the Prince’s family. My father died fighting Dark Legions at the outskirts of Kalpan before they razed the city to the ground, killing my mother and sisters. My two brothers died trying to break siege of Inilpan laid by Dark Legions month earlier. By then, families of other Princes were already extinct, murdered by the Legions.}

His voice raised as he continued almost screaming

\say{As I am the only remaining legitimate heir to the Sceptre of Ezeek, it is my sacred duty to restore greatness of our nation! Or die trying, like my ancestors, in glorious battle! In the name of All Gods and by the sacred power bestowed on me by people of Ezeek, I judge you fully responsible for the atrocities committed by the Dark Legions under your command against my nation and I sentence you to death!}

Ferin took a breath. I considered the accusations. The boy seems to have pretty solid ground, provided he wasn’t lying about his royal ancestry or took it for granted without much substantiation. Now I must carefully lead him through certain inconsistencies in his worldview, before he will be ready to swallow the bait.

\say{Speaking of judgment and sentences, my dear Ferin, don’t you think I deserve some degree of due process and fair trial? Like being able to defend myself, at the very least. Because your side of a story, no matter how true, is told from the perspective of an interested, hence biased, party.}

\say{No court in the right mind will ever consider\dots}

\say{And we do not need a court. If I am not mistaken, we have a Cradle Priest here.}

Battle mage startled and looked at me in a mix of horror and disbelief. I bet he regretted joining these adventurers at least thousand times. Or, perhaps, he alone of them all understood pretty well that I can just kill them all at once faster than they could blink. And the fact that I do not do so and not live up to my reputation in this particular case, made him even more nervous.

\say{But how are you supposed to \dots ?} Ferin inquired.

\say{Priest, I demand the invocation of the Judgment of All Gods.}

I looked aside and a chalice and a knife floated from the shelf to the table.

\say{By the blood I submit\dots Be my witness.} I cut my palm and a few droplets fell into the chalice. \say{By the blood I submit\dots Be my advocate.} A few more droplets. \say{By the blood I submit\dots Be my adjudicator}.

I levitated the chalice to the other side of the table and the quartet looked at it with rather dumb facial expressions.

\say{I do not understand.} The fur hat spoke for the very first time. \say{What is the point of all this show and theatrics? You kind of like to play cat and mouse with us here? It’s not like you are bound by any “judgments” of this sort, aren’t you? What’s there to prevent you from just killing us all should All Gods reach a verdict you happen to not like?}

\say{Nothing,} I noticed. \say{But if I wanted you dead, you would have been dead long before you even reached the Citadel. The guards spotted you right on the city-line.} They looked at each other, visibly surprised, but did not comment. \say{Therefore, one could surmise, your death is not among my immediate priorities. Alas, this is the fundamental failure I so often observe among so many young people nowadays -- namely, the path from point A to point B lies between these points. And if I set out from A towards B isn't it very likely that B is my destination?}

The quartet looked even more puzzled than before. I mentally caught myself prone to "villain monologuing" and had to stop myself.

\say{Never mind. Let's put it simply: I give you my word. I very well understand what reputation I have in your eyes -- that of a ruthless and barbaric tyrant, and it may even be true, but a liar I am not.}

Still none of them moved or said a word. They knew and felt that something was very wrong, and the very awkwardness of the situation completely ruined their mental models of me in their heads.

\say{All right, let us assume that your meaningful silence indicates some sort of preliminary agreement to the overall procedure. I am sure the Priest will provide necessary details later as well as observe and maintain a degree of fairness in this particular confrontation. May I begin my defense?}

Priest startled again and moved his gaze from the chalice to his hands. He was, almost literally, the embodiment of "being uncomfortable" concept.

\say{Dear Ferin,} I started, \say{you claim to be the only legitimate remaining heir to the Sceptre of Ezeek. But are you totally sure this is true? Because last time I checked the political landscape of the Nation of Ezeek, there were five to six different, respected and ancient dynasties in the power struggle for the Sceptre, and, to the best of my recollection, the descendants of the poor Enceris were not even considered as entries to the contest.

Moreover, for a supposedly true legitimate heir to abandon his loyal subjects and embark in a dangerous and lengthy adventure like this and not take at least a company of, say, royal guard or something? So much for the bravery of fearless warriors\dots or were there just no one who believed in you? I bet none of your present companions are of Ezeek origins, aren't they? How did you say, hold on, the "sacred power bestowed on me by people of Ezeek". I wonder if people of Ezeek even aware that they bestowed anything upon you or you just made it up to sound legit and impressive.

Do not get me wrong, my boy, your motives and intentions, without a doubt, are righteous and beyond reproach. You just kind of forgot to mention that Princes of Ezeek tribes are not entirely hereditary titles, but rather a periodically reelected positions. If a House of the Prince dies out for whatever reason, a new Prince from another dynasty of the same tribe is elected.

All things considered I must come to a conclusion somewhat unpleasant to you. That is, having realized that your survival in the Great Winter War alone does not warrant you even the restoration of your former princely privileges, let alone candidacy for the Sceptre, and that your tribe will surely elect another family for its Princedom representation, you decided to put the Heroic Feat at stake. The Ezeek general populace typically consider the political maneuvers of the competing dynasties too boring to follow or sympathize because they do not see the differences between them, if there are any. And, frankly, popular support was never a major factor in deciding on the wielder of the Sceptre. But the Heroic Feat is entirely different thing. Bring them the head of their mortal enemy, bring them \textit{freedom} from oppression and let them believe that this was the true source of their suffering and it is no more, and the common folk will unconditionally hand you the Sceptre overnight.

I must admit, this was brilliant plan. And it may have worked, if only you have given a thought of \textit{who} you will be trying to kill. Speaking of it, may I ask you what was the original intended outcome of your assault on my premises? I am under the impression that at least two of you wanted to kill me.}

\say{I said, I have sentenced you to death for your crimes,} muttered Ferin.

\say{But just a few moments ago you said, to quote, that your sacred duty is to restore greatness of your nation. May I ask you how my death would have served that purpose?}

\say{The Dark Legions have proven to be, and still constitute the major threat to the lands of Ezeek. This threat have to be eliminated in order to prevent anything like Great Winter War from happening ever again.}

\say{Yes, that sounds reasonable, but my question still stands -- how exactly my death would have prevented the Dark Legions from waging war against the land of Ezeek?}

\say{Are you taking me for a fool? No army would launch a campaign like that all by itself without its supreme commander!}

He was angry, felt like being underestimated and morally justified. Perfect material.

\say{Quite the contrary, in fact. I am taking you for a future Prince of Ezeek tribe, and, who knows, perhaps the wielder of the Sceptre itself. Unfortunately, my boy, you are in obvious need for some unpleasant lesson concerning the works of nature and society, which I shall deliver in a moment.}

I took a deep breath. I need to tread this one very carefully.

\say{As you yourself said earlier, the Ezeek tribesmen are known for their generosity and hospitality far beyond their native lands. One can only wonder why, to quote, bravery and fearlessness of its warriors are also known far beyond their native lands. I just happen to have a theory explaining that in great depth and detail but to understand it you will need some levels of education not readily available within the boundaries of our realm, so I will put it in much simpler terms.

You must be aware of the Shallow Strait that connects the sea of Ezeek to a northern ocean and that this strait is frozen during winter and for the most part of a spring. I believe you are also aware of the fact that it was noted long ago that the sooner the pack ices at Shallow Strait breaks the more fertile fish and crops seasons follow. And vice versa, if the ice remain unbroken into mid-summer, the fish does not spawn in your waters, its harvest volume drops and all kinds of droughts begin to occur far inland.

Consider also that there are no trade destinations to the north and west of major Ezeek ports and that tribesmen south of High Peaks levy heavy taxes on your shipping.

%%% I am leaving this here just for the reference of how ecosystem at Ezeek sea and inland territories work.

% about two thirds of Ezeek territory lies in the rocky highlands and are unable to support steady subsistence farming, let alone sustainable cattle husbandry. Also, the Ezeek sea remains frozen well into late spring at these latitudes so navigation can not be opened until then. No trade destinations lie either to the north or west of major Ezeek ports. Combined with the fact that fish production volumes also suffer from the annual climate variations, it is quite expected that total food supply varies annually as well.

% Let me put it in simpler terms. Every four to five years the ice layer covering the Shallow Strait between northern ocean and Ezeek sea grows so thick it remains unbroken well into mid-summer, and when it finally breaks, the sea and air temperature are already high enough that the icebergs melt completely long before they reach the latitudes of Kalpan valley. The high salinity in the upper sea layers thus prevents most species of fish from entering the major valley rivers upstream for spawning so they turn back and spawn in the rivers to the south of High Peaks. As a result -- no fish for poor Ezeek fishermen.

% For the very same reason the northward warmwater circulation current does not restart at summer until, at least, Shallow Strait pack ice is broken and massive cold saltwater inflow from northern ocean displace the deep layers of the much warmer current at the southern Ezeek sea, pushing them closer to the surface. Until that happens, the temperature of the current does not rise, evaporation decreases and the eastward winds blowing from the sea over Kalpan valley and much of Ezeek inland territory do not carry enough moisture to precipitate. The germination of crops is delayed by at least two months and they can not ripe before northern winds start blowing over again. And even if the winds are seasonally delayed, the lack of moisture causes drought and you can not save your harvest by irrigation because that would entail the use of already seriously depleted Kalpan river system. What is worse in this situation is that even if salinity levels make Kalpan rivers accessible, You have to make a choice -- either let fish spawn in the valley in early spring and let your harvest die later or save the harvest but block the fish from spawning there when it had a chance.

% Bear in mind, my dear boy, that this is very simplified explanation as we are still far away from knowing the works of nature in such a minute detail. Sometimes fish do manage to spawn in the Kalpan valley but the rains are still mostly absent, sometimes the opposite happens. It largely does not matter.

So the general picture is as follows. Every six to seven years the glorious and prosperous tribesmen of Ezeek find themselves quite hungry with no apparent means to alleviate the problem. You do not have trade routes across your land to tax them but you pay taxes to your neighbors for shipping, you have no minerals, gems, gold, ores or timberwood to offer for a trade with your neighbors. What you do have, though, is a relatively large fleet of fishing boats easily convertible to pirate schooners able to reach south of the High Peaks in no time and quite considerable bunch of brave and fearless warriors eager to venture southeast where other people just happen to have more fertile lands, lesser dependence on the whims of the nature, and being not so skilled in open combat and stronghold building.

This, my dear Ferin, is the true source of richness, prosperity and glory of the sacred land of seafaring tribes of Ezeek, blessed be their Princes. It had always been so and it is only natural that the basic survival did not interfere with any ethical qualms. Well, up until when the southeastern tribes just had enough of your piracy and raiding and had called for the Dark Legions to protect them from the likes of you.}

\say{What? This cannot be true! The Kings of upper Inilpan have suffered from the Great Winter War just as much as we did -- they could not possibly have \textit{invited} you to interfere on their behalf!}

I smiled.

\say{It is called politics, my boy. The art of lying while knowing full well that everyone knows you are lying and then lying nonetheless. Of course they say they suffered just as much. And it is a mere coincidence that the total export volume downstream the Inilpan had steadily increased for five years straight now. All the while you went lurking around nursing your childish revenge plans.

By the way, I am not finished yet. That part was concerning the true nature of the "former glory" of Ezeek tribesmen. Let us turn our attention now at the Dark Legions.

You know, boy, I am once again find myself deeply offended by your assumptions. I do not like to surround myself with incompetent fools whose only merit is to merrily agree to whatever stupid idea I come up with. The Great Winter War lasted for two years, remember? Guess how many times I personally have been to the frontline? Not once. I trust my generals because only the people I trust can be my generals. Even if your pathetic warband were to somehow kill or neutralize me, the Dark Legions would not automatically disband and run away in panic -- they are not mere slaves held together by forcible imposition of my evil will. They are professional, well trained, well supplied and well paid standing army. And there are contingency plans distributed among every top army officer and every important government official detailing actions and measures to be undertaken should I meet my downfall prematurely. Rest assured, none of said actions and measures are anywhere near what you expected them to be.}

Ferin looked completely stunned. I was beginning to worry that I am supplying the information he needed way too fast. We have got to take a break.

\say{Ferin!} I called. He looked straight at me. \say{The war ended five years ago. At any time I could have turned the whole Ezeek into a barren wasteland. But I did not. Do you now understand why?}

For the first time since the party burst in, Ferin appeared in deep thought. His hands covered his face and his comrades were tactful enough not to bother him now. I almost felt pity for him -- the boy suddenly had too much information to process and acquire and, much worse, too much information previously held true to reconsider. But if he is truly a descendant of Ezeek Princes, he can manage it. Rulers in denial do not live long.

\section{Family Matters}

\say{Alice}, I whispered. \say{Would you mind a few words in a relative privacy?}

She stood and strolled along the table, taking the chair next to mine.

\say{Yes, daddy?}

\say{Stop that, please. Tell me, what exactly is happening here and now?}

\say{Hmm\dots To the best of my observational knowledge,} she started putting serious face, \say{it appears as if a vengeful, ambitious and morally justified hero supported by his faithful friend, wise mentor and comic-relieving sidekick is leading an expedition to strike at and eradicate the evil Overlord and free his numerous oppressed subjects from said oppression\dots}

\say{Your sense of humor is excellent as always, Alice,} I interrupted, \say{but please stop shit-talking me. You of all people know full well that despite the silver shades touching my hair for years now, I am still very able to dispatch the whole battalion of people like Ferin single-handedly by magic alone. And speaking of magic, only the \textit{other} High Magisters can hope to endure one-to-one duel against me and get out of it alive and in a single piece.

So tell me, who convinced these three pour souls that their attack stand any chance at all? No, I know who, tell me why!}

But Alice kept silent, smiling mysteriously and mockingly. I sighed and mentally reviewed the events of the last thirty minutes. There has to be some clue to what is happening.

But of course. I recalled the figure of Ferin sitting on the floor, his back against the wall and almost childish expression of surprise and offence on his face and Alice kneeling beside him, asking if he was injured\dots And then Ferin holding her hands in his and calming her impulses. Well, hello, lovebirds.

\say{Are you engaged with Ferin?} I inquired. The fact that there were a Cradle Priest in their warband suddenly appeared to me from rather unexpected angle.

\say{That is none of your business!} hissed Alice, putting all of her willpower not to blush and failing at it miserably.

\say{Actually, it is. I am still your father, I do not recall us officially disowning each other and by the tradition of our people and by the Common Law you both have to ask for my blessing.}

\say{I do not need your blessing! I am an adult, I am not anyone's property and I have a free will of my own! And I can date, sleep with, engage and marry anyone I damn well please!} She looked at me as if I was about to take away her favorite toy.

\say{My dear girl, you have been absent from this home in general and from my company in particular for far too long. You seem to completely forget how things like that are dealt with here.}

Oh shit, that sounded so menacing and threatening. I did not intend for that.

\say{I mean, what makes you think that getting my blessing will be a big problem?}

\say{I do not care how big of a problem it will be, daddy. My life do not belong to you anymore.}

\say{Alice, stop it, please. You make it sound like I am claiming some sort of property rights over you. I am not. My dear, your recurrent insitence on stressing your independence via adulthood alone is kind of undermined by the fact that it was you, not me, who ran away from parental home, leaving on me the burden of lonesome existence right when I desperately needed the company of someone I love and care for. That is, the only dear person in this world remained after your mother departed to the better worlds. But you ran away, enjoying your newly acquired adulthood as an excuse and escape means from the dire situation in which we \textit{both} ended up. It is not like I am complaining that you abandoned me in exactly the moment when I least expected it, but that is exactly what you did. This is anything \textit{but} being a responsible adult. This is still childish and just selfish.}

\say{It is not like you did not know where I was all this time. You could have easily brought me back any day you wanted.}

I sighed. Kids these days\dots They do not understand what a responsibility is until they have kids of their own.

It is often said that females, unlike us all logical straightforward males, tend to think in emotions and communicate in hints and allusions rather than statements and facts. Damn you! Do I have to spill this out straight?

\say{Yes, but I wanted to be your father, and not your captor! I wanted to earn your respect, not command it! Is that so very hard to comprehend?

And I am still in possession of your inheritance, by the way.}

Tick-tock, clank-clank. Oh, these precious moments of my life like watching my beloved daughter drop her jaw in the shock of sheer magnitude of what has just been said and heard.

\say{But do you\dots Am I\dots But how do we\dots} The rush of thoughts apparently far exceeded her capacity of speech at this moment. I waited patiently. \say{I honestly did not think of that.}

\say{I honestly do not believe you for a second, my dear girl. Am I to assume that either you did not know the heritage laws of our domain or that you volunteered to participate in the conspiracy of these wannabe assassins without ever giving slight thought of who is to sit on the throne next should your plan succeed? I tend to find both assumptions offending my intelligence. And yours, for that matter.}

\say{Wait! Stop! Let's get this straight. You are openly admitting my involvement in a conspiracy to depose or kill you and at the same time you are sitting here talking shit about my inheritance! How is that even possible?}

\say{Wrong question, my dear. You should actually be asking how is that impossible. On average, during the past hundred years alone, seven of every ten rulers on this continent died from conspiracy by close relatives. Of these seven just three died having been murdered by their siblings and remaining four were slain by their own offspring. I can see a pattern when there is one.}

\section{Court Adjourned}

Alice walked back. Ferin, finally having reached some decision, sighed heavily, stood and said

\say{I must admit that your clever words had sown some seeds of doubt in my mind. If what you said of Kings of Inilpan and other southeastern tribes is true, and I will take serious measures to know that for sure, then your intentions in the course of war stand at least some moral grounds. Your actions, however, did not! Parts of our land remains taken, the other parts devastated, our fleet diminished and there is not a single Ezeek family who have not lost a husband, a brother or a son in a Great Winter War. Their spilled blood still calls for justice! And the justice will be served.}

He took his dagger and cut his palm, clenching his fist above the chalice. I observed

\say{Before the justice is served, let it be known that while you wanted vengeance for the fallen, I had to correct nature's mistakes. These ends rarely meet, if ever. During the five years that had passed since the end of Great Winter War, the Shallow Strait remained ice-locked twice more often than usual, and a drought occured again over lands of Ezeek and fish disappeared from the rivers of Kalpan one more time. And yet, despite the inability of Ezeek tribesmen to mount either pirate or overland raids as usual, this time the famine did not struck. Your national pride will not like this solution, of course, since you were raised in the paradigm of "I shall take what I deem is mine" and the idea of negotiations for humanitarian aid is some centuries ahead of your political culture. But so far no one had anything better, so we shall make do with what we have got.}

\say{By the blood I submit\dots Be my witness.} Ferin glanced at me, his facial expression completely unreadable. \say{By the blood I submit\dots Be my advocate.} Alice and fur hat looked at the chalice as if in trance. \say{By the blood I submit\dots Be my adjudicator}. The Cradle Priest took the chalice in his hands and closed his eyes, murmuring an incantation. Everyone waited silently.

This was the riskiest part of the plan, since I have no control whatsoever of the outcome of the Judgment of All Gods. The Judgment was the ancient magical ritual discovered by the early mages. Not only no one knew what kind of evidence and testimony the All Gods take into their consideration to produce a Judgment, but the very concept that this ritual even constitutes a Judgment based on the material presented by the parties -- remained largely open question. It might as well be some sort of a board game. Likewise, throwing a pair of dice might produce equally relevant Judgment for all we know. Or, ripping the heart of a prisoner of war to tell fortunes on it, for that matter.

Therefore the tradition has it bound to the interpretation by the Priesthood. This Cradle Priest must have served at least thirty consecutive years of his civic duty -- a timeframe long enough to acquire some sense of self-preservation along with certain degree of flexibility in his interpretations as not to incur too much wrath and disappointment from either common people or powers that be. And this will be the first cornerstone of legitimacy I expected from him and it is about to appear from the blood chalice. A whole lot of future efforts now depended on how much experience the Priest had acquired during his service and whether or not he caught enough glimpses of my plan to play along with it.

\section{Up To Interpretation}

The Priest stopped murmuring abruptly, the chalice trembled and with a loud cracking sound a bright column of flickering blue sparks fired from it to the ceiling, hung there for a few moments and crashed back into chalice. In a few seconds another cracking sound and another column of sparks burst up, this time bright white and began slowly drifting towards Ferin, fading one by one as they touched him. We all sat in silence, waiting, but the chalice did not indicate any more signs of activity.

\say{The All Gods rule in favor of Ferin, son of Enceris,} said the Priest. Now it was my turn to accumulate all my willpower and put it into the most stone face of all stone faces that have ever stone faced. \say{The White Mark ascertains the purity of his heart, honesty and clarity of his intentions, weight and trueness of his accusations,} continued the Priest, \say{and the All Gods shall deliver the justice as follows. The All Gods rule against the Lugen, son of Adaxos and find him guilty as charged. The Blue Mark ascertains the malice of his heart, fallacious nature of his intentions, futility and failure of his defense.} Besides the very fact of my defeat, all of this fancy wording was just a formality. The important and hardest part comes right now, when the Priest should interpret the very vague and symbolic "verdict" of All Gods in a very specific action of punishment. For a brief moment, I wished they brought someone with the rank of at least Temple Priest.

Meanwhile, the Priest continued, \say{\dots the All Gods shall deliver the justice as follows. The blue shade of the Mark signifies heavens in the blue sky as the position of power above all earthly matters and dwellers. The abrupt crash of a heaven signifies relinquishment of the said power. The All Gods rule that Lugen, son of Adaxos, must step down.}

Tick-tock, clank-clank. Oh, these precious moments of my life like seeing something I carefully crafted finally come to fruition. The quartet looked at me in horror. I relieved my stone face from duty and just sat there for a few seconds, looking absent-minded, reminding myself that I should not, at any cost whatsoever, turn this tragedy into a farce.

\say{What?} I asked them, \say{why are you looking at me like that? Oh, I am so sorry, Ferin, but I am not planning to die anytime soon. Should you decide to press this matter, I would not be so compliant, mind you. But other than that, isn't it what you all were hoping for? I gave you my word. The despot is deposed. The tyranny is lifted. The oppressed cheer in joy,} I almost said "and they happily lived ever after", but this was a bit premature, and, honestly, I did not want to jinx on that, \say{You have got what you wanted, haven't you, idiots?}

\section{Departures}

I stood and turned on my "business-boring" voice. \say{It is quite late in the night, by the way. Given the newly discovered circumstances I kindly ask you all to stay at these grounds as my honoured guests until, at least, tomorrow morning. Please, use the exact way you entered here to return back to the Inner Court of the Citadel, where my castellan will greet you and provide you with living quarters, medical assistance if needed, food, drink, hot bath and whatever else you might reasonably need at this time of night. As a gesture of my good will, your weapons or whatever remained of them will not be forfeit. But I strongly discourage you from any attempts to refuse my hospitality at least until the sunrise. Have a good night, and excuse me -- I have plenty of work to do,} I waved my hand and the entrance door slammed open. The warband, throwing concerning glances towards me, retreated. On the edge of my perception, I overheard the fur hat say \say{If this is some perverted form of execution, I\dots}, slapping sound and Ferin's angry \say{shut up}.

Of course, I could not have resisted the temptation of a little farewell practical joke. The castellan was ordered to provide fur hat and the Priest each with regular single-bed room, but a luxurious double-bed honeymoon-styled apartment for Alice and Ferin. For a brief moment I considered ordering a ceiling mirror installed above their bed but then decided it will be just too much. Alice was not kind of a girl easily pushed and might ruin the intended outcome just because she felt being contrary.

There is just one facet to the today's story remained unclear before the circle of inevitability is started. I descended to the Inner Court and walked to the door of Priest's quarters. He was not yet asleep, so I knocked and entered a bit unceremoniously, took the chair and sat by the table. The Priest sat on the bed reading some books. He glanced at me and said in shaking voice

\say{High Magister\dots}

\say{Oh, drop it, Priest. We are alone here, no need to keep the theatrics before commoners. Just speak. How did they buy you?}

\say{Buy me?}

\say{Convinced. Talked into. Threatened. Bribed. Promised. Whatever! What is the reason you find yourself in a warband like this? Did you not understand the risks? Even at the maximum mercy I could possibly extend towards the perpetrator and make the city watch overlook it completely, premediated assault on government institution with battle magic as part of an armed group is still a major criminal offence and in violation of who knows how many rules in the scripture corpus. Your Temple will strip all your credentials right away and you will no longer be able to employ yourself even as a janitor monk anywhere near any other Temple. From then on, your only career path will be the mage mercenary or unlicensed healer, and we all know full well their average life expectancy in the line of service is counted in mere days.

There has to be \textit{something} very special for a Cradle Priest to risk everything for and I demand to know what it is!}

\say{High Magister, my motivation is plain simple and far less ulterior than it looks. But please do not tell the others, I do not want them feel guilty over it. My Temple will not strip me of anything because my Temple was the one in Darbash, one of two northwesternmost temples completely destroyed in the course of Great Winter War, the other one being Xubash. I defended my Cradle with everything I have got but these\dots they had some weapons specifically against the mages, some magical artifacts which ripped our eyes and ears inside out and did horrible things\dots we could not stand it\dots and we ran away, abandoning our Cradles. They captured the Temple Priest, tortured and killed him right there inside the Temple, desecrated all our Cradles and then razed the temple to the ground. Today you would not even guess where it once stood.}

\say{They -- who? Dark Legions? I know nothing of such weapons.}

\say{No, not Dark Legions. The Ezeek-Sukhai raiders, the northernmost Ezeek tribe. They do not believe in All Gods, they have a variety of demonic cults, all ruthless and bloodthirsty so much so that even their fellow Ezeek from other tribes regard them as a barbaric cavemen and are afraid of them and their war shamans.

Darbash is currently occupied by the Nation of Ezeek. We have petitioned the city authorities and Ezeek dynasties for permission to rebuild the Temple but they were all denied, even though Darbash was always a frontier of spreading of the All Gods culture. You see, the faith of All Gods is seen there as a crawling cultural assimilation threatening their ancestral beliefs. They think that you, High Magister, spread the faith to the lands beyond your realm and then conquer them under the pretext that they constitute the one domain of All Gods.

This is why all of Ezeek tribes look suspiciously at All Gods missionaries, albeit not as extreme as Ezeek-Sukhai who just kill them outright but still we are definitely unwelcome on any Ezeek grounds.}

\say{This is interesting. Makes me wonder why our dear Ferin took his very personal communications with the All Gods without as much as a flinch.}

\say{Oh, but you do not know how he survived the Great Winter War where all his family perished?}

\say{Enlighten me, Priest.}

\say{Ferin is now twenty seven years old. He was twenty when the war started. Of these twenty he spent last fifteen years living in Port Dauruna, where he moved with his aunt at the age of five when Prince Enceris sent him to gain the most modern education your domain has to offer. He never went to war. It is unclear if he wanted to but I know the Prince Enceris expressly forbade him to return. Therefore, it has been at least twenty two years since Ferin last time set foot on any Ezeek soil. I bet he would not be able even to name complete Ezeek pantheon, let alone truly profess the ancestral faith. He grew up and spent all of his adult life so far in the culture of All Gods.}

\say{What a dimwitted slimy asshole. I admit, his nationalistic sentiments almost got me convinced. "To restore the glorious Nation of Ezeek", my ass.

But wait a minute, how do you know all this? It is unlikely that Ferin confessed such intimate and very undermining details of his biography to you. I don't doubt your talents as a confessor, but letting this kind of information loose is far too dangerous for any future political career.}

\say{No, High Magister, he did not confess. It just happened that a few of us former Priests of Darbash had settled up in Port Dauruna in civil service for the municipal authorities. And some of us there were assigned to help a local Ezeek diaspora to manage supplies for Ezeek refugee camps. Ferin's aunt was prominent social and humanitarian worker there at the time, everyone knew her and sought her attention. At times like that people in need are very talkative so the Priests learned the biographies of entire Enceris dynasty in virtually no time, and in far more details than official sources can afford to be. We still keep contact with each other, sharing important information, and we thought that surviving member of Enceris family might come handy eventually. Especially now that his aunt had departed to the better worlds and the Nation of Ezeek still have not concluded on the wielder of the Sceptre.}

\say{I see\dots But this is still just one part of the picture. It almost explains why did you took the risk, but does not explain what for.}

\say{I am just a humble servant of All Gods, High Magister. I know my limits and do not aspire above what I can handle. During all my life all I did was to help people overcome their spiritual and earthly problems. But there have been some sort of universal opinion among Temple Priests that the former Darbash and Xubash Priests are not to be employed in any temple on a positions higher than grounds keeper. As if it was somehow our fault that we did not stood for our Temples to death, or sacrificed ourself uselessly for our Cradles which will have been desecrated anyway\dots I serve All Gods, not Temple Priests, and I have my pride, High Magister. And my pride tells me it is wrong and unfair for me to sweep dirt at the Temple doorsteps when I can and want to save lives and give hopes by the Cradle.}

\say{So much for the humility of the All Gods servant, huh?}, I intervened, \say{I definitely remember some scripture teachings on the subtle difference between pride and hubris when it comes to the Temple services. "Do not envy the foundation of the divine house: a smallest nail is struck last but fails first".}

\say{Yes, but another paragraph of the same chapter reads "In dire times Evil beseech for inaction of the righteous". High Magister\dots are you challenging me for the scripture dispute?}

I laughed and said \say{No, I was just checking your theoretical training. Never mind, go on with your story.}

\say{So they, Alice and Ferin, approached me in the tavern at that time when I was particularly disenchanted in my miserable life and could only walk on my eyebrows and they started to ask questions and tell various promising stories. Like they are of a royal descent and personally disliked the Temple Priests and their policies, and if only they were to gain some tangible power they would see to it that Priests like me are treated fairly and with respect and so on. Of course I did not believe them at all and told them to piss off and leave me alone. But next day as I sobered up Alice showed up at the same tavern and challenged me to prove her to be impostor by any means necessary, betting large sum of money if I succeed. Of course I did not. Then Ferin appeared with pre-war volume of "Royal Encyclopedia of Ezeek" and tried to do the same but by then I was convinced and ready to venture to hell itself if that should save me from my misery.

Their plan had me clearing the path into your throne chamber, that is, I should blow up the gates of Outer and Inner court and any locked door they may encounter inside the sanctum. I may have stunned a few guards on our way as well. After that, either their plan was somewhat vague or they decided not to let me into its details. I surmise they hoped to either somehow force you into surrender or kill you, counting on the assumption that you would hesitate to harm your own daughter and a heir to foreign kingdom. The rest you know, High Magister.}

\say{And you seriously agreed to the assault plan of this sheer stupidity, knowing full well what a High Magister is capable of?}

\say{They did not ask for my agreement. I sort of had not much of a choice, High Magister. At any rate, my life could not have ended up any worse than it already was.}

I stood up, stepped towards the door and said \say{I will see to it that you are employed as Cradle Priest at the Temple of All Gods in Rosemeadow district. But you should remember at all times, Priest, that this is not a mercy, nor a pardon but a deal on a quid pro quo basis. And should I or one of mine appear with a specific request within your capabilities, I will not tolerate any ethical qualms or excuses like that the righteous people of your kind are particularly prone to. Do not worry, I shall not ask you of anything that brings you disgrace, but other than that consider yourself at my service first and at the Temple service second.}

\say{Thank you, High Magister.}

Back in my chambers, I looked down on my table, where the large sheet of paper rested, empty.

\say{Beware of premature conclusions,} I mentally said to myself, \say{you have not heard her side of a story yet.}

The thought occurred to me that, perhaps, I should keep it that way rather than discover just how much of her daughterly love amounted to "four out of ten rulers fell by the hand of their offspring" statistics.

I took a stylus and wrote "The Decree".

% \royaldecree{I, Lugen XII, by the will of All Gods steward of these united blessed lands and protector of their peoples, do hereby declare the following:\dots}
