% \chapter{The Grand Setup}

\section{Life Of A Dream}

Alice yawned and stretched under the blanket of enormous size but decidedly did not want to open her eyes, let alone rise from the too soft bed. It has been months since she had an opportunity to sleep on anything but rough straw-filled mattresses or, sometimes, her own cloak laid on bare ground.

Ferin was still sleeping on a couch across the room. Alice did not want to be too accessible too soon, his interest and advances towards her needed some warming up and proof of persistence. She would not throw herself in the hands of any would-be Prince from distant postwar hellhole kingdom, abundant with nothing but enormous nationalist pride. After all, she was of royal descent, too.

There was a careful knock on the door. Alice opened her eyes, quickly reached under the pillow and grabbed a dagger. One can never be too safe.

\say{Come in,} she said.

The door opened and two busy-looking past-average aged women entered, stood at the foot of Alice's bed and bowed deeply. Their clothing was richly sewn with gold threads and they both wore silver medallions with Lugen's family crest embossed on them.

\say{Good morning, my Lady,} they said synchronously. Then one to the right continued, \say{I am Bertha, the head of your Administration Chamber and this is Ursula, the Housekeeper of the Citadel. We\dots er\dots did not really wanted to interrupt your rest but there are several very pressing bureaucratic matters not addressed in the decree of your predecessor,} she reached in her pocket and produced a notebook and a stylus. \say{Namely, the issuance of royal assents and dissents to public petitioners as well as many other document workflows in the Administration Chamber have been suspended pending approval of your royal formal and informal title, styling, address and formal name, possible alterations to the royal stamp and motto if needed, et cetera.}

\say{My Lady, Inauguration planning session should also be scheduled as soon as possible,} intervened Ursula, \say{so we need firsthand update on the current political situation, that is, as of this moment, whether the Nation of Ezeek is considered by the throne as hostile, neutral or friendly, as well as the political status of its heir apparent}, both women synchronously glanced towards still sleeping Ferin and Ursula continued, \say{whether there will be a royal wedding ceremony coincident with inaugural or a separate one}.

\say{If I may be of help, my Lady,} intervened Bertha, \say{I may suggest some options to restart and expedite the governance process. Since the foundation of your dynasty there were six reigning Alices so according to tradition your formal name may be Alice VII. Of six reigning Alices four were styled as Queens, one as Empress and one as Grand Duchess. Speaking of titles, if you were to continue the tradition laid down by your predecessor, it would be Dark Overlady as informal title, and "by the will of All Gods stewardess of these united blessed lands and protectress of their peoples" as formal title; finally an address style has to be approved both for formal correspondence and for addressing by your subjects and guests, you may go as "Your Majesty", "Your Grace" or any qualifier of your choice. Please, my Lady.}

Alice sat on the bed hugging her knees and staring at both women with eyes wide open. For a second time in less than a day, the inflow of information completely overwhelmed her consciousness.

\say{Wha\dots What???} she squeaked, \say{my what?! Predecessor? Chamber? Wedding?! Inauguration?! What the hell happened here?! Explain away!}

\say{Of course, my Lady,} bowed Bertha, \say{by the decree of Lord Lugen XII, by the will of All Gods steward of these united blessed lands and protector of their peoples, he relinquished the throne and stepped down from all positions of power within said blessed lands, thereby declaring the Inheritance effective immediately, that is, about five hours earlier. Since you are the only known heir of Lord Lugen, you have now assumed almost all the aforementioned positions except the chair at the Council of High Magisters which will remain vacant for the time being. Your positions are: Lady Alice VII by the will of All Gods stewardess of these united blessed lands and protectress of their peoples, supreme Lady commander of the Dark Legions, Grand Admiral of the Dark Fleet, Lady protector of the Faith and Overseer of the Temples, the President Benefactor of the Royal Academy of Arts and Sciences, the Chairman of the Council of Guild Masters, and a number of lesser positions most of which are honorary and require little to no attention. By now, my Lady, the whole peoples to the farthest extent of the blessed lands are aware and eager to pray for and congratulate your\dots err\dots Majesty Queen Alice VII on your ascension and wish you the long and prosperous reign.

My Lady, what is with the names and titles? I need to restart the governance or by evening the Citadel will be buried under the paperwork.}

\say{Go with the defaults}, replied Alice, \say{bring us some breakfast. And find me an office well lit with good view around and with a soft and comfortable leather chair. The very thought of sitting on that ugly chunk of metal makes me cold.}

\say{At once, my Lady. Anything else?}

\say{Yes,} Alice seemed to have regained her confidence completely, pointed at still sleeping Ferin and asked \say{how many people in the administration know who he is?}

\say{Only us, Your Majesty.}

Alice rose from the bed and looked at them attentively, then asked \say{Keep it that way, then. But how did you know that?}

\say{We have received specific instructions from Lord Lugen in a letters accompanying the Decree,} said Ursula.

\say{I want to see them,} said Alice.

\say{Unfortunately, Your Majesty, it is not going to be possible. The letters bore a Seal of Nondisclosure and burned away once we read them.}

\say{Of course\dots All right, that is it. I expect a breakfast in ten minutes,} said Alice and went to the shower room as both women departed, bowing.

\section{Identity Crisis}

When Alice entered the bedroom again, Ferin sat on his couch with rather confused look on his face, observing considerable variety of dishes on a golden plates and golden utensils on table right in front of him. Alice took a chair, sat behind the table, took the utensils and looked inquiringly at him, saying \say{What's wrong? You better eat all of it, we have a lot of work today.}

\say{Good morning. What did I miss?} asked Ferin looking at the gold, \say{This level of luxury can't possibly be extended for a guest-prisoners, am I right?}

\say{Oh, you missed a lot. First of all, for a supposedly stereotypically romantic knight-like character you like to portray yourself to be, who swears his absolute loyalty to me and professes his undying eternal love each time you want to have sex with me, you missed at least two unexpected and unannounced intruders who might have been assassins. So much so for, to quote, "ever watchfully by your side", you sleeping beauty,} Alice took her time to chew on food, watching Ferin's face reddening in ever more confusion.

\say{Other news,} Alice continued, \say{I am now Her Majesty Queen Alice VII, Dark Overlady, by the will of All Gods stewardess of\dots err\dots shit\dots I have got to memorize this. Anyway, from now on, I am the rightful supreme ruler of the Dark Domain, Dark Legions, Dark Fleet, this Citadel and pretty much everything that is around, including number of other fancy things and entities whose names I also have got to memorize, I guess.

And no, this is not a joke. I would not be joking about that since I find this absolutely not funny at all.}

They kept eating for a few minutes in silence, building tension, then Alice finally said. \say{All right, what is it? You do not seem to have been particularly impressed or surprised by this big news.}

\say{Why should I?} asked Ferin, his voice unusually quiet, \say{Lugen lost the Judgement, promised to step down, kept his word and acted accordingly. You are his only known heir and within full legal rights and capabilities to inherit the throne. It is only logical.}

\say{You are happy for me, aren't you, Ferin?}

\say{I am. Congratulations on your ascension, by the way. Long live the Queen,} said Ferin with the voice more appropriate for delivering an eulogy.

Alice pushed the golden plate away, turned towards Ferin and banged her hand against the table, saying \say{Enough of this shit! You will never have me in your bed unless you stop pretending to be little fragile girl easily hurt by the innate injustices of this world and a snail which would rather cower than speak your mind openly! I now have an entire domain to babysit and I expect a tangible \textit{support} from you, not having to babysit you as well!}

Ferin turned towards Alice too and covered her hand with his palm. He looked bemused, his eyes were very sad as he looked at her.

\say{Support? And what kind of support could that be, exactly? Alice,} he said, \say{Do you remember how it all began, all these years ago? How did \textit{we} began? Do you even remember what we were trying to achieve back then?

I do remember. Before I met you, I felt incomplete, partial. And it is not about my feelings towards you. It is about my ambitions, the very definition of what I am as a person in this world, what I am able to prove myself capable of doing, my ultimate reponsibility for making at least some part of this world a bit better than it was.

And in the very rare occasions when you seem to speak your mind honestly and openly, I saw it in you that you felt exactly the same. That there is some drive inside you to prove your worthiness to the world, to your father, to anyone who dares doubting you, that you are someone to be reckoned with.

In these moments I felt like we complete each other, we are two missing pieces of the puzzle of this world, who together make up more than one obscure corner but rather complete the entire picture with some important new quality.

Now, where did it all go?}

\say{Did it go?} asked Alice caringly.

\say{Did you hear what your father said yesterday before I decided to partake in the Judgement of All Gods?

He said, basically, that I was nothing, an empty space, no one believed in me, no one knew I exists, no one supports me, no one cares if I achieve anything or not, that I am now the distant remnant of the once glorious family now forever forgotten! A complete and utter failure! And it all was true, every word of it, he immediately saw right through my pathetic deception! And he did not even use magic for that, all it took is a bit of observation, logical analysis and a piece of Ezeek newspaper on politics.}

\say{Whoa, whoa, stop right there, boy,} said Alice raising her palms in denial. \say{First of all, I do not remember him saying these exact words. He just voiced some concerns about your credibility as a potential player in the political landscape of Ezeek. Your chances there as you stand today are ineed minuscule, but that is no secret and it had never concerned you this much before. What happened now?

Secondly, come on, Ferin. Do not take his words too literally. You would not expect him to praise and glorify someone who just minutes ago burst into his throne chamber with apparent intent to kill him. Such level of cynicism is beyond even my father. He had to punish you for it, if only by such humiliation. All circumstances considered, you ended up very lucky through this ordeal. By lucky, I mean alive and in a single piece. Cheer up.}

\section{Second Revelation}

\say{I don't know, Alice. Your words make sense as much as his words do and that confuses me even more. I am totally gullible and totally lost.

And look at you. I remember very well what you said back then when we decided to go together. That he raised you more as a heir to the throne and less as his beloved daughter. That your mother was the only source of any warm feelings, love and care a family must be cemented with. And that when she departed to the better worlds you ran away because of exactly that -- you could not anymore stand being treated as an instrument of function rather than dear and close soul.

So what changed since then? Oh, he handed you his power on a plate. Decided that you are finally ready after all these years he spent schooling you to be his successor ruler. Made sure the complex clockwork of Dark Domain is greased to the specs and is in a competent hands.}

Alice very gently touched his lips with her fingers and said in a soft quiet voice \say{Ferin, please don't say that. It is not true, and it is more complex than you think. I had some conversation with father yesterday before you had the Judgement of All Gods commenced. He is much more human than I previously thought. And a very tired one. My running away actually made him suffer and I am feeling guilty over it.}

\say{This is called a manipulation, my dear Alice -- imposition of guilt on someone to make them help achieve one's own ulterior goals. Parents are prone of it just as well as the others. And I already see, from the way you look and talk, that you took this bait seriously, that you plan on ruling the Dark Domain thoroughly and already mentally sorting the order of envoys and ambassadors you shall meet today in the most politically effective order.}

\say{What is your problem with that, Ferin? Would you rather me refuse? Ding-dong, fresh news -- I did not have a choice! He was within his right to decide on it personally and unilaterally, he wrote an Inheritance Decree this night and I woke up today's morning already a Queen Alice VII and there was absolutely nothing I could do about it. And you know what? By law, I can not even abdicate the throne until I produce a heir of my own!}

They suddenly stopped, glanced at each other embarrassedly, Alice blushed and Ferin abruptly leaned forward. Their eyes closed, lips touched and for a few long seconds nothing else mattered in the slightest.

Then Alice gently pushed Ferin away, and smiled, saying \say{Don't get too used to it, lovebird.}

Ferin blinked for a few seconds, restoring his grasp to reality and said \say{What I wanted to say, Alice, is that I believe we both lost our way. The way we envisioned together when we started it years ago. Up until today we supported each other because we could not walk the way we chose and achieve our ambitions without each other's support and encouragement. To an extent we were a role models for each other. And now what? This much power and responsibility handed to you overnight means, first and foremost, that you will no longer find any time whatsoever to be yourself, not Dark Overlady. You do not need my support anymore since there is full Dark Domain at your personal disposal, and I can not rely on yours because your position essentially depersonalize you and I am bound to be on the bottom list of your priorities, no matter our personal affections.

Your father was right. It is over, Alice. This is the end.}

Alice leaned back on the chair and thought deeply. First, never before she witnessed Ferin in a depressive mood of such magnitude under the least stressing circumstances. Second, never once either of them had ruled out her eventual ascension to power, including, but not limited to, as an instrument to achieve own goals. Why would this all of a sudden pose a problem, and what kind of a problem exactly -- Alice did not understand. Third, judging by the arguments he just invoked about not needing a support and his priorities being not on top of everything else\dots What an asshole. "This is called a manipulation -- imposition of guilt on someone to make them help achieve one's own ulterior goals?" Exactly what is happening here. Ferin is being jealous and manipulative jerk, fearing that the world, represented by Alice, would stop revolving around his dearest enormous ego any time he felt like it.

But, apparently, there is more to it than that. His concerns were at least partially genuine. His strangely misplaced reference and sheer emotional overreaction to Lugen's yesterday humiliating speech about his future political career in Ezeek is definitely suspicious and could indicate Ferin did not tell her everything there is to know about it. How she could help him achieve that goal is unclear, unless\dots Unless\dots Unless seven years ago the Dark Lord launched a successful military campaign against the Nation of Ezeek and through means less than humane in general, bent the circumstances to his will.

Alice tasted the idea of starting another devastating war just to have one pretty handsome but very manipulative jerk to feel needed, valued and appreciated. The idea tasted bad. Let's rethink it from there. A full scale offensive is not needed, per se. We will not be facing combined Inilpan and Ezeek forces this time, even though the last time it was a ruse on behalf of Inilpan rulers.

One Dark Legion at most will be sufficient to deter any tribe warlord, if needed and to demonstrate the seriousness of Overlady's intentions and demands. Now what could those be? Install Ferin, son of Enceris as Sceptre wielder? They would behead him as a traitor and collaborator as soon as Dark Overlady returns home. And she could not stay at Ezeek because\dots Because why? Because that would be a standing occupational force and every merry bonus that comes with it like sabotage and guerilla warfare.

No, it would not work at all. Any enforcement would not work at all. At least, in the long run. But, what her father had said yesterday? "Bring them the head of their mortal enemy, bring them \textit{freedom} from oppression and let them believe that this was the true source of their suffering and it is no more, and the common folk will unconditionally hand you the Sceptre overnight", he said. Bring them the head of their mortal enemy, huh? That would be me, thought Alice. Check. Bring them freedom from oppression. But wait, I'm not oppressing them yet. Check. And let them believe it is no more? Like how? Uncheck. All right, it was Lugen, not me, who oppressed them, that one they will understand. But I can not possibly credibly demonstrate to Ezeek that "Lugen is no more", let alone his head as "head of their mortal enemy". That is just beyond impossible. Unless\dots What did Ferin just say? "your position essentially depersonalize you", he said. Depersonalize. Alice tasted the word. Meaning, the job dissolves your own identity making you as yourself indistinguishable from your position. Can this be a solution? Solution. Ha-ha, pun intended. Bring them the head of their mortal enemy. Not the actual Dark Overlord or Dark Overlady in person, but their dissolved, depersonalized selves. And make it big enough they choke on it. 

The Dark Domain itself. That was it. Embrace, Extend, Extinguish. The idea struck her like a lightning. This will work.

\section{Necessary Micromanagement}

There were just a few technicalities to be solved, and first technicality sat right in front of her in a deep depression and almost crying over his self-perceived uselessness. All right, it seems an appropriate time for some domestic violence. 

Alice stood up and said in her most menacing and threatening voice, \say{You will owe me forever and dearly for what I am about to do for you, but only this time,} she swung her arm and landed a heavy slap on Ferin's back of the head, \say{Listen up, asshole! Next time you try to cry me a river over your inability to find purpose in life or failing to achieve it, I will just agree and kick your sorry ass out!} yelled Alice, landing another slap on Ferin's head, \say{Now shut up, suit up, and follow my every order unconditionally, which you actually must do within my domain anyway!}

Eyes wide open but not saying a single word, Ferin quickly dressed up and stood in front of her, looking down.

\say{Wait outside, I will be in a moment,} said Alice and he left. Dressing up, Alice vividly remembered how her father once shared a piece of his wisdom she did not understand at the time, saying \say{"Freedom and adulthood are similar in that they both are \textit{not} an ability to do what you want. Freedom and adulthood are different in that true freedom is a right to not do what you do not want, while adulthood is an obligation to do what you must towards those who do not yet (or already) possess either quality.}

Alice went outside and looked around, expecting\dots Aha, there he is. \say{You are to show me into my office, am I right?}

\say{Yes, Your Majesty}, said young servant, \say{Please, follow me.}

They crossed the square inside the Inner Court. Ferin gasped in surprise, looking at the brand new, polished and shiny entrance door to the Inner Court, looked as if they did not blew the previous one to slivers just a night earlier. Nothing indicated the attack ever took place. Ferin wondered how many people today actually knew that it took place.

To a mild surprise of Alice, they did not enter the sanctum. A minute later, ascending stairway of snow-colored marble, Alice finally verbalized what seemed wrong with the situation around them.

\say{Where is everyone?} she inquired, \say{I remember the Courts to be rather crowdy places but now I have only seen like five guards in a hidden niches and a two or three page-boys carrying something.}

\say{There actually are not many people in the Citadel, Your Majesty,} replied the servant, \say{They are mainly employed in the Administration Chamber and in keepers house, but that is on the other side. During the regular workdays, such as today, most of them do not need to go about Citadel grounds since the Lord Lugen decided it causes a huge waste of time. Rather every employee is provided with a necessary number of servants at his disposal.}

Finally they entered the room, and every aspect of it looked absolutely opposite that of the Lugen's throne chamber. Gigantic windows, dazzling blue and white marble decorations, grape vines hanging from the special ceiling hooks and tethers, and in a corner, a fountain. With golden fish.

A long table and a two dozen chairs stood in the middle of the room and at the far end the table was crowned with massive leather chair with elaborate decorations and a family crest.

\say{This could not have been built overnight,} mused Alice, \say{therefore there has to be a reason for the Dark Citadel of the Dark Overlord to have this little girl's playground.} She walked down the table, sat in the chair and declared, \say{This is perfect}.

\say{You,} she said to the servant, \say{I will see Ursula, then Chief of General Staff, preferably with some maps of northwestern territories, then Ambassador of Nation of Ezeek, and then whoever is in charge of Royal Protocol. And you,} Alice pointed to Ferin, \say{wait outside until I am done talking to Ursula.}

The Housekeeper of the Citadel showed up in almost no time, bowed and said, \say{Your Majesty?}

\say{Take a seat,} Alice pointed at the closest chair, \say{Tell me, how important is the Inauguration politically?}

\say{Not particularly, my Lady. Traditionally, only the rulers who were not confident enough in their right to the throne or did not gain enough popular support sought to stage a show of power and wealth with elaborate details and rituals. It is still prescribed in the Keeper codex as a part of formal enactment of the ascension, but, legally speaking, the Inheritance Decree is much stronger legislation. Actually, the last time a full-scale Inauguration was staged by your great-grandfather, Lord Odonis.}

\say{How much did it cost then?} asked Alice.

\say{Accounting for inflation, today it would be about a four hundred thousand crowns.}

Holy shit, thought Alice. This was nearly unimaginable amount of money. For four to five crowns a day one could afford a decent breakfast, dinner and supper, pay for a room in a good hotel and there will still be a change left for some souvenirs.

\say{This is not that much as it sounds,} observed Ursula, \say{especially in comparison to the other budgetary spending like military or urban development.}

\say{All right, how about this. No inaugural show. To celebrate the ascension of their modest and beloved Queen, Her Majesty decided to issue an one-time royal gift of a comparable amount of crowns distributed evenly among the city populace, per person. Have it ready for the next round of monthly taxation.}

\say{Excellent idea, my Lady.}

\say{Now, did you receive any special instructions concerning my\dots ahem\dots \textit{other} associates?}

\say{Yes, my Lady. They were given some amount of money, strong suggestion to avoid any further association of this kind lest they are tired of their own heads upon their shoulders, and set free, per Lord Lugen's order.}

The old man is indeed getting soft, mentally noticed Alice. Is he still haunted by the past this much?

\say{Where is he now, by the way?} inquired Alice.

\say{No one knows,} replied Ursula, \say{no one has seen him since tonight's events. And I have a feeling he would not reappear in the Citadel anytime soon, my Lady.}

\say{And one last thing Ursula, since you asked this before\dots There will likely be a royal wedding. It is just not yet clear when, and I am talking of months, probably a year. It is not to be announced yet, of course, but I wanted to give some advance notice to you to avoid surprises in the future.}

\say{I understand, my Lady.}

\say{That is it for now, Ursula. Have a good day.}

\section{Wargaming}

General Nhusen in a black uniform with just a few shiny metal trinkets appeared in the doorway carrying a briefcase, saluted and followed Alice's gesture, sat on the chair by a table. Next came Ferin and sat on the opposite side.

\say{General,} Alice began, \say{assuming I know little to none about the causes and the course of Great Winter War, would you mind delivering a brief lecture on it?}

\say{Sure, Your Majesty. The general idea begind the military invasion of northwestern territories was conceived by Roraz, then reigning king of Eternal Kingdom of Inilpan, also known to us as upper Inilpan, when they faced ever growing problem of Ezeek raiders. Despite upper Inilpan being four times as large and harboring three times as much population as Ezeek, the Inilpan failed to mount ground forces of any significance and had no ocean-going fleet. Before the war, the Dark Domain had no terrestrial border with the Nation of Ezeek -- the Inilpan gap between the closest points along the western shoreline stretched to about two hundred miles.

Roraz negotiated with Lord Lugen asking him to intervene militarily into Ezeek lands to cap and restrain their radiers activity, promising attractive trade agreements and concessions in return as well as support of All Gods missionaries in Inilpan. Essentially, Roraz wanted to force Ezeek to legitimate trade only. But he also wanted to preserve good standing with Ezeek Princes who, despite covertly encouraging the raiders, officially condemned them publicly and had each their own lucrative trading agreements with Inilpan. Because of this, Roraz must not have been seen associating or aligning militarily with the Dark Domain, so he reasoned that he could not simply allow Dark Legions through his lands as this would clearly indicate a conspiracy, and so Dark Legions had to stage an attack on some parts of Inilpan territory as well.  Attacking Ezeek from the sea is nearly impossible -- the logistic supply lines are almost three times as long and under a constant threat of the tribes south of the High Peak.

Hence the disposition of the forces at the beginning of the war,} -- General reached into the briefcase, took a map from it and laid it on a table, \say{Army Group A at the western parts of the border advancing in northwestesrn general direction and supported by Dark Fleet if necessary, and Army Group B in the vicinity of Xubash advancing towards the northern parts of the Kalpan valley.

According to the general plan, both army groups would seem to "cut" about one sixth of the Inilpan territory, least populated and scarce with anything valuable. Group B were to present credible threat to the Roraz capital city by advancing upstream Inilpan river but then "unexpectedly" turn westward to help main invasion forces of Group A. Had everything gone according to a plan, both army groups would join at the general vicinity of the Kalpan delta, besieging the strategically important city of the same name.}

General Nhusen sighed deeply and continued, \say{It was expected that at this point, having two thirds of Ezeek territory occupied, trade routes completely cut from the major ocean ports and just two months ahead of winter, the Princes would be hard pressed to negotiate a deal favorable for us and King Roraz.

But no war ever goes according to a plan. It is always like a forest fire -- you put out one burning piece of it to find two more by the side and a third just behind you.

Just a day after Group B left Xubash and began advancing along the Inilpan river, the intelligence reported that a large Ezeek expeditionary force was spotted near Darbash moving eastward, threatening to cut supply lines and appear in the rear of Group B if left unattended. Roraz panicked and demanded that we attack them right away with everything we have got or else they would reach his capital in under two weeks maximum. We had to improvise. The Ezeek army was so numerous that at first we decided that it constituted the combined raider forces of all tribes readying for major assault against the upper Inilpan. The Group A was split in two subgroups C and D, one continuing the advance along the shoreline the other, composed of the more mobile cavalry units intended to reach the rear of Ezeek army at about the same time as returning Group B would set an ambush at the ferry posts on Inilpan river just north of Xubash. They were to attack simultaneously, splitting Ezeek forces in two and inflicting maximum possible losses.

For reasons still unknown, the Ezeek expeditionary forces attacked and took Xubash -- a city barely big enough to accomodate their troops and of next to nothing strategic importance. The ambush on the other side of Inilpan made no sense, approaching subgroup D was not nearly as large as needed to lay a proper siege. We had completely lost the initiative of the war having captured none of the objectives. Meanwhile, the scouting units of subgroup C had spotted \textit{another} large Ezeek expeditionary force, just a bit smaller than the first, this one advancing towards the eastern side of Kalpan valley to threaten upper Inilpan from the north.

Had they been left unattended, both Ezeek army groups, striking from the north and south would have easily eradicated the entire kingdom of upper Inilpan for good. At that moment we had the only strategic advantage over them in that Ezeek commanders thought we were still advancing through Inilpan gap, "fighting local resistance" or suchlike. They did not know that both of our army groups were already this deep into Ezeek territory and considered our troops they spotted near Xubash ferries as some sort of advance parties unable to mount serious offensive. Apparently, they planned to take Roraz capital, join both their forces and still have enough time to catch us at the rear, cutting supply lines and beating the Dark Legions completely.

Finally the General Staff had enough, recalled subgroup C and D ordered them to reinstate into the army group A and mount an all-on frontal assault on Xubash while Group B was crossing the Inilpan river back to the western bank. This was the first major battle of the Great Winter War. In a day, remaining Ezeek forces fled Xubash to join their second army and from then on the general course of the war completely lost its simple planned elegance, turning into an apparently random skirmishes at apparently random locations. But that happens everytime with each war, so no surprises.

Suffice it to say, that despite the significant drawbacks and heavy casualties at the early stages of a war, by the next year's mid-autumn we were able to finally besiege Kalpan as planned, forcing Ezeek dynasties into negotiations. By that time almost all of the raider forces and strategic bases were eradicated, the official Ezeek standing army devastated to pieces and what remained of them and the raiders, went into deep forests engaging in exhaustive guerilla warfare and sabotage. At first the dynasties refused to surrender, maintaining that exhausted and tired Dark Legions would simply not survive another winter with our logistic supply lines stretched as thin and long to the Kalpan and under constant attack of guerillas, but their stance soon worsened when we successfully reached a deal with the tribesmen south of High Peak that they would not attack our supply convoys if we allowed them to capture one southernmost Ezeek port, at the time under our control. And so the supply began by the sea and we were finally able to perform massive rotation and relief of the troops with fresh and battle-ready contingent. By that time Ezeek already have their fleet largely destroyed so when King Roraz joined the negotiations and offered them cheap credits, extensive food supply and humanitarian aid programs, the dynasties began to accept the terms. It, however, took them almost three more months to negotiate the territorial claims but finally, this is what we have got as of today,} -- General flipped the map to the other side and began pointing to various areas on it, \say{What remained under our control is the Inilpan gap and this stretch of land along the northern High Peaks and up to the ocean. Inilpan royal family is still very angry at us for having lost access to the ocean from the port that does not freeze at winter, despite having unlimited tax-free access to services of five other Ezeek ports up to the Kalpan delta, as well as tax-free shipping and transportation rights on most of Ezeek territories except Kalpan valley and the southwest. Ezeek kept the Kalpan delta but had lost the upper valley and the mountains to Inilpan. Darbash and Xubash provices are under Ezeek control as well.

This is basically the reason why it is said that Roraz was the only winner in this war. We gained territories that are of no use to us -- our native ports are larger, more technically advanced and do not freeze in winter. No one want to move to settle by the High Peaks voluntarily, as these lands are the most subjected to climate-based harvest variations. Ezeek had their army and economy destroyed now completely depending on the supplies from Inilpan, drowning in debts with every year but restoring what little production capabilities they got. It is only Eternal Kingdom of Inilpan that gained and multiplied their wealth as a result of our involvement, even though we put considerable reparation payments over them -- actually, the only known case in history when the winner pays reparations to the loser, however doubtful the qualification.

That is about it, Your Majesty.}

Alice looked at Ferin. His face was gloomy and pale. \say{I guess, the history taught at the Ezeek schools is entirely different,} she thought, \say{no one would admit that their own neighbors had fed up with them and jointly started a war to put an end to what you proudly considered your national tradition. It must be very hard to see it from this perspective.}

\say{Very good, General. Now,} asked Alice, \say{assuming we will be facing a need to enforce a few more or less political decisions upon the Ezeek dynasties, such that they will be hard-pressed to accept\dots In your opinion, what it would take military-wise?}

\say{It is rather hard to say, Your Majesty. Depends on the seriousness of our demands. But a single Legion can be re-stationed at Kalpan outskirts in under a week and it will amount to the force still larger than what the entire Nation of Ezeek can muster now.

But if I may, Your Majesty, there is a much better option. Our agreement with High Peak tribesmen still stands, and if we surrender the Inilpan gap back to the Eternal Kingdom, this would not preclude us from being able to reach the Ezeek but in return we could ask the Inilpan King to exert an arbitrary economic pressure on Ezeek dynasties. And believe me, this will be far more persuasive than any number of Legions stationed by Kalpan. The pre-war Ezeek Princes were warriors but today's dynasties are more concerned with debts and incomes than military honor and courage.}

This statement seems to have struck Ferin at the very heart of his national pride. He slowly rose from his chair and began menacingly, \say{How dare you\dots}

\say{Shut up and sit down!}, said Alice loudly. Ferin stood for a few seconds silently and then sat back, breathing heavy.

\say{Thank you, General, that would be it for now. Have a good day.}

\say{Your Majesty,} General stood, saluted and left.

\section{A Game of Deadly Hints}

\say{What is it? I let you sit here and listen so you can \textit{learn} the truth and not give me a show of insulted pride!}, hissed Alice at Ferin.

\say{Alice, I am honestly, to the best of my abilities, trying to comprehend what it is that you plan to do with me, I still have not a glimpse of idea,} complained Ferin.

\say{It is fine. Just sit there, listen, think and do not speak unless I tell you to. You will begin to understand soon enough.}

Doors opened again and a merrily looking man stepped in. Or rather rolled in. He was moving like happy puppy when his owner gets back home. His smile was almost visibly illuminated the environment. He immediately began, \say{Your Majesty, it is a great honor to finally meet you! I am glad that you picked my humble personality prior to my colleagues from other ends of the world. Perhaps I should take this as a sign of some affection, but without a doubt this indicates a very special relationship between our countries, to their mutual prosperity and longevity.}

\say{Welcome, Ambassador Tam. Look at this man opposite you and tell me if you know who he is.}

With a somewhat surprised look on his face, Ezeek Ambassador considered Ferin. Ferin returned the look with visible disgust.

\say{Your Majesty, this must be none other than Ferin, son of the late Prince Enceris. My boy, you have grown a lot since these old times in Port Dauruna, haven't you? Oh, Your Majesty, you are scaring me. Is he here to replace my humble personality at your service?} inquired Tam.

\say{Not at all, Ambassador Tam. But I would be extremely grateful to hear a story of how and when you got to know each other. Because it seems that our dear Ferin here, albeit usually very talkative about adventures of his early youth, had completely omitted any mention of your existence. We shall alleviate this problem, shall we not?}

\say{Oh, Your Majesty, do not blame the boy. The youth today, you know, do not really remember who they were talking to just yesterday. And a very few people indeed have memory as good as mine. Frankly, we have met only three times during all these years, so no big surprise there.

First one was about twenty years ago when his beautiful auntie asked me to write a letter of recommendation to help with his admission to the Royal College of Port Dauruna. My goodness, Ferin was only seven years old but had already managed to impress me with his deep and extensive knowledge of calculus, astronomy, construction engineering and suchlike. His enormous technical talent obvsiously felt too constrained by that little scrawny figure.

The second time was on the day of his graduation with distinction from the Dauruna University. I was invited to attend by the University authorities and, completely coincidentally had a letter for him from Prince Enceris. Though the letter was sealed, the Prince himself told me what it was about. It was the onset of what will then become known as the Great Winter War. Enceris made me promise I will try my best to keep the boy away from it. And it is not like I did much in that regard -- his auntie was not only beautiful woman but also very intelligent, caring and gifted with foresight.

The third time was on her funeral. A very, very sad day for our Nation regardless of where we live in this world. There are not many Ezeek women who had helped so many souls and saved so many lives and was never hesitant to get her hands dirty. I remember on that day our dear Ferin was in the company of a certain young girl, though, but it could not possibly have been Your Majesty, could it?}

\say{Ambassador Tam! For a politician of your expertise and experience, you have unusually long and loose tongue, haven't you?}

\say{Oh, Your Majesty, I pledge to the contrary. You see, there are certain situations incompetent people tend to get themselves in, that provoke reactions and assessments inherent to a regular human being than that of an experienced politicians.

For lack of better explanation from Your Majesty I interpret the presence of our dear Ferin as a hint to that he may play an important role in the future relations between our respective countries. After all, unimportant people are rarely seen by the side of the reigning rulers of the Dark Domain. Rest assured, that reluctance of the dynastic Council of the Nation of Ezeek to settle the situation is inciting discontent even domestically. So much so that non-member dynasties may soon find themselves in a position forcing them to officially declare the Council incompetent and seek for some other \textit{practical} solution. Should it be the case, I will promptly notify Your Majesty about the timeframe of the said "soon", who is likely to be deciding the aforementioned practicality at the other side and other important details.}

\say{But Ambassador, I thought you have to act in the best interest of the Nation of Ezeek? But what I just heard from you, if done exactly that, would, theoretically, amount to Grand treason and conspiracy with foreign powers to usurp the Sceptre\dots}

\say{But \textit{I am} acting in the best interest of the Nation of Ezeek, Your Majesty. That it may somehow match with your best interest too is rather lucky coincidence, an opportunity which would be very sad to miss. The legality is always relative, especially when it comes to ancient traditions, and you will be surprised just how many of my compatriots tend to agree with that nowadays.}

\say{Thank you, Ambassador, it was a pleasure,} said Alice, watched as he departed the office then turned towards Ferin and looked at him inquiringly, \say{So\dots Port Dauruna, huh? Royal College? Graduated from University with distinction? What should I expect next, Ferin? I definitely have a secretary of Royal Academy of Arts and Sciences in the list of visitors today. If you are standing member of the said Academy, I would rather hear it from you now.}

Ferin was silent and looking down

\section{To Be Continued\dots}