\chapter{The Building of Bridges}

\section{Enter the Reason}

The mission of the Dark Domain was humble. The squad of heavily armed cavalrymen as the advance guard, followed by His Excellence Special Plenipotentiary Envoy of Dark Domain, followed by pair of his official advisors, the mission Keeper and his servants all mounted on a durable and winter-hardy horses, followed by two supply wagons and, finally, by the squad of heavily armed cavalrymen as the rear guard.

Looking at the monotonous landscape around him, Ferin struggled to find any feeling of joyous reunification with his homeland. Apparently, none of dirt, stones, snow, ice and gravel shared his enthusiasm on that matter. Ferin remembered little, if at all, of his childhood years here, having spent almost five times as much in the Dark Domain. It was already too late to feel nostalgic.

When their mission neared Kalpan city, Ferin was surprised to find out it lacked Citadel or any castle-like building worth of capital prominence. The feeling of surprise reached its peak when the whole diplomatic mission was housed in a hotel.

Next morning the reason for such generosity became apparent for Ferin when they approached the Kalpan town hall -- a building three stories tall and barely large enough to hold an infantry battalion of its defenders. The very administrative center at the capital of the Nation of Ezeek was smaller than one single dormitory of Dauruna University and only the banners and ornate decorations on the facade hinted at its special government function.

Accompanied by his official aides, Ferin ascended ornate stairs to the third level and briefly stood before massive wooden doors. The doors slowly opened and the herald yelled \say{His Excellence Special Plenipotentiary Envoy of the Dark Domain on behalf of Her Majesty Queen Alice VII, Ferin, son of Enceris!}

Ferin entered the chamber and approached large oval table at which about a dozen people sat and watched him with utter curiosity. The elderly man opposite the Ferin stood and said \say{As Interim President of this Council, I welcome Your Excellence at our meeting. Please, have a seat.}

Ferin took a seat at the table and his aides sat behind him. One of the men spoke \say{How was your trip, Your Excellence?}.

\say{Uneventful,} replied Ferin, \say{Please, let us spare no time to small-talk.}

The Interim President chuckled and said \say{Your Excellence, even though we are more or less aware of the good will and benevolent intentions of Her Majesty, the protocol mandates that you make it officially clear firsthand before us all.}

\say{Gladly,} replied Ferin. \say{Her Majesty Queen Alice VII believes it to be very unfortunate circumstance that despite the fact that atrocious war have ended more than five years ago as of now, our respective nations did not yet had a chance to officially settle the dispute and disagreements in a mutually beneficial manner. Her Majesty also believes that all sensible and reasonable deferrals are now due and there is virtually nothing that precludes the Dark Domain and the Nation of Ezeek to sign a peace treaty.}

\say{With all due respect, Your Excellence,} voiced the Interim President with grim look, \say{it is not under the authority of Her Majesty to ultimately and unilaterally decide when the time is up for the decisions of the sovereign and independent Nation of Ezeek concerning its foreign policy, especially in the troubled times like these.}

\say{Her Majesty respects the sovereignty and independence of the Nation of Ezeek, of course, and have no intent to influence its foreign policy in any unwelcome way}, continued Ferin, \say{And I beg you to understand that I have only duly conveyed the thoughts and assessments of the Dark Overlady on this matter.

It is, however, can not be ignored that the issue now extends beyond the realms of pure diplomacy and into the area of the very credibility and trustworthiness of the power structure of our respective countries.}

\say{How so?} inquired the Interim President.

\say{By the simple and inevitable fact that until the peace treaty is formally signed, the Nation of Ezeek and the Dark Domain are still officially in the state of open war against each other. Do not think for a second that Ezeek common folk had completely overlooked this part, because they did not and it clearly endangers their well-being.

Next summer the raiders will likely regain enough strength to start attacking southeastern territories again\dots}

\say{We do not endorse, supply, encourage nor exercise any control over the so-called "raiders"}, intervened one of the seated men.

\say{Of course you do not}, continued Ferin, \say{they are just purely accidentally follow your plans whenever the large and supposedly uncontrollable force is needed to advance your interests without moral repercussions; and this is exactly why your standing army is somewhat smaller and underequipped than the city guards in the capital city alone. But I digress. The reason why the resurgence of raiders is much more dangerous and much less wanted today is exactly as aforementioned. Now that Dark Domain and Nation of Ezeek share some common border and Dark Legions are not formally restrained against conducting retaliatory strikes against the illegal armed groups, it makes Ezeek commoners seriously doubting your credibility as the governing body concerned for the safety of its subjects.

To put it in simple terms, the people are ready to declare the Dynastic Council incompetent and remove it.}

\say{There is no legislation permitting such removal, Your Excellence. Moreover, the Dynastic Codex allocates as much time to chose the wielder of the Sceptre as needed. Your concerns and worries on the matter are unsubstantiated.}

Ferin stopped for a moment, considering what he just heard. Is this man delusional? Or was it just a thin diplomatic game?

\say{Emran}, Ferin asked, \say{I do not want this to turn personal, but, please, drop the charade and be reasonable. Did the residents of Port Aldan needed \textit{any} legislation to hang the governor upside down on a nearby lantern and rip his stomach out?}

The Interim President Emran flinched and grimaced as if in pain. The strike was indeed too personal -- the late governor Tarcis, murdered in such gruesome way, was his grandfather. But Ferin had no intention on being soft on these old farts.

\say{Ferin}, said one of the men at the table, one of the younger members of the council, \say{You are essentially threatening us with the popular uprising. I can not help but wonder why your earlier stated intentions disagree with your arguments to achieve the supposedly desired outcome. We can reasonably assume the Dark Overlady has enough tricks at her disposal to provoke some tribes to open revolt but you just said she wanted to sign a peace treaty. Don't you see there is a certain contradiction?}

\say{I do not}, replied Ferin this time with stronger metallic undertones in his voice, \say{The Dynastic Council which fails to produce the wielder of the Sceptre for five years straight, is impotent to say the least. Her Majesty could have overlooked this fact alone had you produced any executive body with which to negotiate peace, but the problem is that the fact is not alone and you had not produced anything. Now, it is not a threat but rather a strategic analysis. Let us all play a thought experiment and try to guess what happens first: either the tribesmen lock the door and burn you alive right here for your inability to secure them against the retaliatory strikes of the Dark Legions on the resurgent raiders, or, perhaps, accept reason, face the reality and act accordingly.}

For a few moments, silence fell on the hall. Then Interim President spoke again, \say{Your Excellence, while it is true, as my dear colleague noted earlier, that we do not exercise control over raider parties, I must assure you that they are not mindless savages, not beyond reason and not above any strategic foresight. They are, in fact, just as much tribesmen of Ezeek as any of us here and by virtue of that they are also negotiable, believe it or not. Especially when it concerns the well-being of the Nation of Ezeek as a whole.

That being said, I, the Interim President of the Dynastic Council of the Nation of Ezeek can and will extend my greatest sympaties towards Her Majesty along with written guarantees that there will not be any cross-border attack of any raider party at least until this Council exercise its duties.}

Listening to that, Ferin stumbled upon the word "negotiable". A special note should be taken about that.

\say{You are missing the point, President,} noticed Ferin, \say{Her Majesty does not need any such guarantees as the Dark Domain is fully and completely capable of defending its borders against any number of raiders. It is your own population that you endanger by holding it hostage for your enormous ambitions and desire for power.

But let us assume for a moment that there was a voice of reason in your promise and that you can indeed persuade the radiers to avoid the incursions in the former gap of Inilpan. But how about the Inilpan itself? Unlike Dark Domain, the Kings of Inilpan are much closer and have a way stiffer economic grip around your neck. No warlord in the right mind would dare stick his nose beyond right bank of the river.

This leads us to a central question -- whom will they be raiding?} Ferin took a breath and looked at each of the council members, \say{You are sitting here in peace believing that it somehow is a result of your previous efforts, but actually you are sitting on the barrel of explosives that could ignite the civil war of magnitude the Nation of Ezeek has never seen, and this barrel is already smoking.

Emran! The Nation of Ezeek is not just a fancy word. It is people. And people are tired, tired of uncertainty, tired of fear, of insecurity of their future. I am very surprised that you are so oblivious to it. Tell me, please, what exactly it is that precludes the Dynastic Council from naming the wielder of the Sceptre?}

\say{It is a classified information, Your Excellence,} replied Emran grimly, \say{And believe me, I and this Council are very well aware of and totally understand your personal concerns for the well-being of the Nation of Ezeek -- of course, everyone knows that you too are the proud son of this land as much as we are.

But the choice was yours and it has been made -- since you revoked your Ezeek citizenship, you are, as a foreign subject, is in no position to direct or otherwise suggest any course of action we may or may not take in order to alleviate any internal political issue.}

\say{I am not a foreign citizen}, calmly replied Ferin, \say{and I did not revoke anything.}

\section{High Stakes}

The younger council member venomously smiled and asked sarcastically, \say{Oh yes, surely the Dark Overlady would employ a non-citizen to be Her Majesty Envoy abroad. It is commonly done, right? Especially in the country like Dark Domain where non-citizens are not allowed to hold jobs better than junior janitor and babysitter.}

This is it, thought Ferin. Finally. The old farts want to play rough, so let us play rough.

\say{Exactly,} confirmed Ferin, \say{because Her Majesty, unlike you, hold reason and common sense \textit{above} traditions whenever it benefits the Domain and its peoples. And it is only logical to employ Ezeek national as a Special Envoy to this land because who else, if not him, will be able to see your sheer stubborness and stupidity from outside point of view?

I am just now wondering whether you are genuinely bluffing or indeed downright stupid. You cited the Dynastic Codex to me today, Emran, but did you actually read it? "Blood Calls", chapter 4, sections first through tenth -- legally speaking there is no such thing as Ezeek citizenship.
% in the sense that could be granted or revoked at a whim of some bureaucrat.
There are only the blood rights and they are unalienable no matter to whom one swears fealty. I do not have to remind you what blood rights are, do I?

I claim the blood rights of Ezeek tribesman and as Ezeek tribesman and as such I am no different than any of you.}

\say{And what exactly is your blood claim, Ferin?} inquired Emran.

\say{At this moment -- none. I am just reminding you that we stand on equal grounds. But that largely remains to be seen and depends on your willing to cooperate and reach mutually beneficial solution.}

\say{All right,} the younger one intervened again, \say{assuming all this is true and you are legally a genuine Ezeek national with the proper blood rights and all that. Still, this fact alone does not qualify you to either be privy to state secrets or to exercise any sort of influence over the Dynastic Council.}

Ferin smiled. One more little push and they will take the bait.

\say{Except if the Dynastic Council itself is assembled on illegal basis,} said Ferin strongly, causing surprise gasps all around the table.

\say{Oh, my boy, may be it is your turn to be pointed at a certain chapters in the Codex,} said Emran with a condescending smile, \say{you can not be seriously challenging the basic dynastic rules. The death of all Princes has happened before in many previous wars and both the precedent and legislation are very specific on the proceedings, authority and the outcome of the Council. There is no mistake,} asserted Emran.

\say{I can not help but wonder how you can say all this looking straight at the son of Prince Enceris,} mused Ferin, returning the smile.

The Interim President began to laugh hysterically and immediately half of the council members joined him. A few moments later, picking up his handkerchief and wiping tears from his eyes, Emran asked: \say{I am sorry, Your Excellence, this was undiplomatic. But, frankly, so was your outrageous idea. Was this the Dark Overlady's devious master plan? To send us her puppet and convince us to give him the Sceptre?}

\say{I value your sense of humor, President,} followed Ferin and stood, \say{but let me make all of this a bit more straight and clear.

You know, the library of Dauruna University is regarded as one of the richest across the continent in terms of the subjects covered. And thanks to large Ezeek diaspora there is no lack of professional teachers in the Laws of Nation of Ezeek. Having considered myself a proud Ezeek national I decided to take a few extra courses in Ezeek Law, including, of course, the Dynastic Codex, just in case I will be having conversation like this in the future. What a lucky foresight, huh?

It appears that you, dear Interim President and members of the Council, are interpreting certain provisions of the Codex rather frivolously, especially those pertaining to the very essence of Dynastic inheritance. Let me remind you of some things any law student, unlike you, will find rather obvious and hard to interpret any other way.

First. The core concept of the Princely Representation before the Sceptre is a dynasty, not the Prince himself. This way, should the Prince die for whatever reason, the dynasty is not immediately dismissed before the Sceptre but rather allowed to elect and present another Prince in timely manner.

Second. If, and only if, the dynasty fails to do so, it may be considered as no longer representing its tribe before the Sceptre but that decision must be approved in a certain order to take effect: first by the tribal assembly, second by the ruling Princes of the other tribes and finally affirmed by the Sceptre wielder himself, although this is a mere formality. If the tribal assembly do not approve the dismissal of the dynasty before the Sceptre it must still assign the Prince-Regent from the same tribe to act on behalf of the deceased until a native Prince can be elected.

Third. The Codex does indeed prescribe the assembly of a Dynastic Council in case of the catastrophic events such as death of all Princes and their dynasties, but strongly maintain that the Council must: ascertain the circumstances of said events and take all and every measure to find any living descentants of the Princely dynasties should they somehow survive and assemble the Council by invoking the delegates from each Ezeek tribe through the corresponding tribal assemblies.

Fourth and most important. Because the Sceptre holds authority over other dynasties as long as at least one of them still exists, \textit{including} that of the Sceptre wielder himself, if a sole dynasty survives, its members take precedence in the holding of the Sceptre, regardless of them having elected their Prince or not. The ruling dynasty thus considered as transitional wielders of the Sceptre until all tribal assemblies convene, reinstating their representative Princes.}

The younger council member glanced at Emran nervously, but the Interim President sat motionless with his eyes closed and listened.

\say{Just in case you need a references to all of the aforementioned,} said Ferin mockingly, \say{it is all in the Dynastic Codex, book "Sceptre of Ezeek" chapters two, five, six and seven, book "On Dynasties" chapters first through eight, and book "On War" chapters fifteen through twenty nine.

And in case you need some precedents to refer to, at my pleasure: the last time Dynastic Council assembled was at the aftermath of the Eastern Kercak empire invasion about five hundred years ago. Then the Kercak emperor managed to launch a surprise assault and capture all the dynasties and their Princes at the summer festivities just below the Inilpan pass and when his demands were not met by the Sceptre wielder, he executed all of the hostages and then besieged and razed Kalpan itself. The surprisingly detailed overview of the proceedings of the contemporary Dynastic Council you may find, in the same Dynastic Codex, appendices three through five. It is a fascinating reading, I admit.}

\say{Your Excellence, we are greatly impressed by your extensive knowledge of Ezeek Law and history, but, please, let us return to the present time,} said Emran.

\say{I am just about to, President}, replied Ferin, \say{I will now just enumerate certain facts that I have observed concerning the legitimacy of the today's Dynastic Council.

First. You should not have declared the dynasty of Enceris as extinct, until after you have ascertained the death or incapacity of all of its members. It was relatively small dynasty, by the way, we were only twelwe people.

Second. You can not claim to be oblivious to whereabouts of the son of Prince Enceris since one of the very men who would have been tasked to find the remaining members is none other than Tam, Ezeek Ambassador to the Dark Domain, whom I know personally and who knew exactly where I was at the time the Council convened. % also who maintained communications with Uluna ?

Third. There were no tribal assembly considering the case of Enceris dynasty as either extinct or concerning the assignment of the Prince-Regent.

Fourth. The implications of the "sole dynasty survival" clause, I believe, is far too apparent and obvious to elaborate.

Fifth and final. The clause of the "representative council" mandates delegate from each tribe of Ezeek. Since the Kercak invasion ended five centuries ago, there are sixteen tribes of Ezeek. You know, having graduated from Dauruna University I believe myself to be able to at least count to sixteen. I can only wonder why I see \textit{thirteen} of you at this table and why, for the heaven's sake, the tribe of Anok is represented by \textit{two} delegates at the same time?

All in all, speaking of following the Codex, your Dynastic Council had knowingly committed at least \textit{four} capital crimes against Pillars of Dynasties as defined in Codex, six to eight grave violations of inheritance protocol, and countless lesser wrongdoings.

Before any of you have any bright idea of telling me that commoners largely do not care about any of aforementioned legal specifics, let me remind you that the very existence of the sovereign country in terms of its official recognition is always a very vague matter. Right now there are two major problems with it.

First problem is that the other countries may find that self-proclaimed ruling body such as yours is not only incapable to resolve prolonged domestic political crisis according to your own laws but also have extremely dubious legal grounds of its very existence.

Second, a state is only considered as sovereign when it has an explicit monopoly on violence on all of its territory. That is, the enforcement of the law throughout the country should be governed by a single body. Now you are saying that you do not control the radiers but they are "negotiable"? But what happens if they just stop listening to you? What if they revolt? You do not have any means to put possible raider insubordination of any kind to an effective and forceful end. This is, my dear members of the Council, is called a "failed state" and is of a major concern internationally as well.

As of today, everything I just said is not yet public knowledge. But at the same time nothing I said and observed constitutes any secret for anyone curious and smart enough, such as newspaper reporter or intelligence analyst. It is only a matter of time before this all is revealed worldwide. If you think you are not accountable to anyone, you are wrong.}

Ferin sat and swiped the sweat from his forehead. This was a far shot and there is a significant chance that it will miss the target. Who better than Ferin knew the stubbornness of Ezeek people. But no war is won in a single battle. His mission today was to sow the seed of doubts in the heads and hearts of the Council.

The harvest will soon follow.

\section{Whims of Hospitality}

The Interim President looked at the other council members one by one, made a heavy sigh and said, \say{Your Excellence, we are definitely very grateful for the thorough and detailed analysis of the current political situation in the Nation of Ezeek. We value your deep insight and strategic thought on the matter in the hopes that it will help both our countries reach the peace sooner. Unfortunately there were several grave accusations brought up during the discourse and we shall see to it that these accusations are investigated duly and properly. Until then, I am afraid, the negotiations may go no further.

Now the Council meeting will continue behind the closed doors. Your Excellence will be invited to continue our peace talks tomorrow. Thank you and have a good day.}

The Dark Domain's mission stood, bowed to the Council and left.

Back in the hotel room, Ferin struggled to hold a cup of hot tea in his trembling hands. The magnitude of what has been said and done today only now descended on him in full force. His aides sat at the table, intensively writing something on a multiple sheets of paper.

He strongly wanted to ask someone for an assessment of his actions today. The desire was almost childish, like the kid's need for approval from adult. But none in this mission was his peer. He was alone and it was depressing.

There was a sound of rushed steps behind the door and a cavalry Captain Krond in full battle gear entered the room, saying \say{Your Excellence, you \textit{must} come with me at once.} The way he said "must" strongly implied the overall situation has now turned from diplomatic to military, in which case his authority is way higher than that of the Special Plenipotentiary Envoy, so Ferin unquestionably followed the captain downstairs. There he was handed a cloak, a sword, a packed saddle bag and a horse and in a few seconds they both were galloping the streets of Kalpan in the western direction.

Once outside the city, the gallop switched to trotting but it was a few more miles before they stopped on top of an elevated hill. Captain Krond dismounted, took a looking glass and looked at the horizon where city of Kalpan stood, then mounted again and their horses resumed the trotting alongside each other.

Ferin knew better than just ask what the hell happened, and Captain Krond felt the moment to be appropriate, saying \say{Your Excellence, I am sorry for any inconvenience our premature departure might have caused\dots}

\say{There is no inconvenience, Captain,} interrupted Ferin, \say{I very well understand that we are on the enemy territory and unless I am pouring syrup over Dynastic Council in the town hall, our mission is essentially military at any other time, so you did exactly what you had to do.}

\say{Thank you for understanding, Your Excellence. But I still owe you an explanation. Our spy ring in the Kalpan city had warned us about imminent attack on your temporary residence which, I believe, is happening at this exact moment as we speak. The nature of warning was vague as to who the perpetrators will be and what their intentions concerning you are, but assuming your arrest is a way simpler job than head-on assault on the mission I initiated a special contingency plan. Right now, several other pairs of riders each consisting of a cloaked mission agent accompanied by a fully armed cavalryman from my squad are fleeing the Kalpan city in different directions -- one pair towards Inilpan pass eastwards, one towards the Xubash ferries, one towards Port Enteek and one pair is headed towards Port Zula.

The second squad and the rest of the mission personnel remained in hotel and are arming themselves to repel the attackers. What happens next is unclear and largely depends on the enemy's chain of command and the swiftness of its reaction. As of now I observe that the western gates to the Kalpan city are closed shut, it is safe to assume the other gates are closed too.}

\say{Holy shit! We are a diplomatic mission, what the hell they are thinking? Attacking a Special Envoy of the Dark Overlady like that is an outright declaration of \dots ahem\dots right. Declaration of the war already declared and never officially ended. Damn. Captain, please, to the best of your knowledge and military experience, can you give me the best and worst scenario for our comrades left behind?} inquired Ferin.

Captain Krond pondered the question for a few moments and replied, \say{Well\dots Assuming the attack is not some kind of a ruse, desperate maneuver, or demonstrative reprisal, that is assuming there is a certain tactical goal and advantage they seek, it mostly depends on whether their agents spotted us and the other rider pairs and had passed the information before the actual attack commences.

If they did spot us in time to report it, their commander must have correctly guessed it to be the cover up for the operation of your extraction. Then the remaining mission personnel will likely be arrested and put in prison to then be used as a bargaining chip or suchlike. That would be the best scenario for our camrades.

If, however, the attack commenced prior to their report, they will likely attack the hotel and kill all of the mission personnel. This will be the worst case scenario for our camrades.}

\say{But Captain,} Ferin felt Krond is not telling him everything, \say{if they did not find my dead body among the fallen, they will correctly assume I had escaped and they will send a manhunt parties after each of the rider pair, will they not?}

\say{Your Excellence,} replied Krond heavily, looking aside, \say{on my orders, in an event of attack the last man standing will trigger the Wildfyre charge. There would not be any bodies to look through.

But you are right, of course. There are chances of manhunt parties sent after us in either scenario. This is why we must hurry.}

\section{The Price of Duty}

Wildfyre. Holy shit. Holy shit! Brighter than midday sun, hotter than any volcanic lava, burning through steel and stone as fast and easy as through paper and living flesh. Unstoppable, inextinguishable, making its long way even underwater. Is it going to extract a heavy toll for someone's betrayal today?

Right before the sun touched the horizon they found a lone cliff hanging above the river with accessible back slope and climbed on top of it. From this distance one can only perceive the reddish hue of the Kalpan city walls and only through powerful looking glass. The big mushroom cloud of thick black smoke hung above the city. The Dynastic Council or whoever else was behind it, received the first retribution payment.

They made camp for night on a hill with large scattered boulders located way off the road with all the necessary security precautions of a men being chased. The camp overlooked the road in both directions but was very hard to spot unless you know precisely where to look. Ferin ate standard military ration with a blank stare, trying to remember the faces of people who accompanied him on this journey. "Uneventful" he remembered saying to the Council. What a greedy, stupid, power-hungry asshole Emran. He will pay dearly for that.

\say{Your Excellence,} called Krond quietly but Ferin was so deep in this thoughts he did not notice. \say{Ferin!} called Krond a bit louder.

\say{What?}

\say{Stop castigating yourself. It would not help. Their death is not your fault. We are soldiers. I am a soldier. It is our job to fight for our people, our country, our Queen. And when there is a fight, there is a death. It is an occupational hazard and every soldier knows it.

It is not the first time I leave my men behind to cover the retreat of the main forces. You can not really get used to it, never. It hardens your soul every time. But they all volunteered, knowing to expect anything. And they died like heroes, in glorious battle, taking many enemy lives for every comrade fallen.}

\say{You talk much like my father, Captain. Down to the exactly same words about heroism, duty of a soldier and self-sacrifice for your homeland. Only, you know, he was telling these same things about them}, Ferin waved his hand in the direction of Kalpan city, \say{what a bitter irony.

And you are talking about soldiers. But there were civilians! They were not supposed to be left behind like that.}

The twilight was already turning into the night so Ferin heard Captain Krond chuckle rather than seen it, \say{There weren't any civilians in the mission, Ferin. Except you, of course.}

\say{What?!}

\say{Yeah\dots Why you are so surprised? It is a common practice since the very dawn of espionage. All of them were the secret agents and officers of the Dark Eye, bound by oaths and fealties far more serious than that of a mere soldier like me. And a few of them even outranked me, I am sure. You have to spend some time in the military to learn to spot these folk right away -- the way they talk, walk, move, and do things are quite distinct for a trained eye.

If that helps manage your feel of guilt, let me assure you that even rank-and-file field agents of the Dark Eye can put up a fight no less serious than seasoned soldier of the Dark Legions. They receive very special training in combat and are masters of any weapon mankind had invented so far.}

\say{I have got a lot to learn\dots Anyway, when you explained where decoy riders went you somehow did not mention Port Aldan among obvious destinations. Does it mean we go there?}

\say{Yes. I reasoned that the Ezeek ports will be assumed by their authorities as the least likely destination for the fleeing Special Envoy. That is, if one does not know there will be a Dark Overlady's merchant ship in each of three ports waiting to bring you aboard.

All right, it is time to take some rest. We stand watch three by three hours, mine is first.}

Falling into sleep Ferin mentally noticed that the contingency plan of this scale must have been confirmed with Her Majesty, who, of course, did not find any reason whatsoever to give \textit{him} any instructions on the matter.

\section{Uncertainty}

Next day, trotting on the road along Aldan river, Ferin kept trying to understand the motives and reasoning behind what had happened yesterday. But it did not add up to anything sensible.

First, who in Kalpan city had the capability to orchestrate an assault on a Special Envoy of Dark Domain and not fear the potential repercussions? This question boils down to the much simpler one -- who really holds any power in the Nation of Ezeek today? The Dynastic Council. The raiders, despite being more powerful military-wise, never engage in political games, covert operations, conspiracies and suchlike.

But what were the motives of the Council? Ferin remembered how Interim President laughed after being told about the single dynasty survival clause written right there in the Codex. Yes, the clause was circumstantial at best and conditional on a number of other prerequisites but it was a strong clause as one directly addressed by the Codex.

Apparently, nor the Interim President himself nor the Dynastic Council gave any shit about following the Codex to the letter anymore, interpreting and skipping parts of it as they feel like. \say{And there I was}, thought Ferin, \say{naive and idealistic moron, accusing them of the crimes against Pillars of Dynasties they committed. Seriously? As if they did not know it already.}

Power corrupts. Absolute power corrupts absolutely. It is not yet clear what kind of social contract was struck between the Dynastic Council and the Ezeek commoners in the aftermath of the war but past five years had proved it to be surprisingly stable setup. \say{I naively thought I offered them peace and resolution of the political crisis,} mentally reasoned Ferin, \say{but instead, it seems, I threatened their political stability, their very source of power. And they reacted accordingly.}

But still it did not explain their rash decision to attack the mission. No matter how power hungry, no usurper will surrender his own sense of self-preservation and will not undermine his own power base. Unless Ferin did not know something very important about the political background of Ezeek, it looked like direct invitation for the Dark Legions to take Kalpan again and this time end the Dynasties for good. And no other sovereign nation will say a word about it after what had happened yesterday. There were hardly an international crime worse than attacking an embassy.

By noon they hid off the road again, because if Kalpan managed to send instructions over signaling towers to Port Aldan this early morning concerning their interception it will be about that time they encountered their pursuers head-on. But the traffic remained regular and civil throughout the day. By evening they finally reached Port Aldan but did not enter the city, instead making a wide detour to the ocean shore just south of the city, where in a certain hidden spot near the ruins of the old beacon they found a rowing boat and through the looking glass confirmed the "Dexterous" flying the familiar dark banners on the roadstead of the Aldan bay. The captain welcomed them on board, and "Dexterous" immediately raised the anchor and headed southwest.

Someone is going to be held accountable for all this.
