\chapter{The Cost of Retribution}

\section{Expectations and Allegiances}

Her Majesty Queen Alice VII sat in her enormous chair, legs on the table, staring blankly at the ornamented ceiling. Today it was the last place in the whole Citadel she would rather be. The first one being, of course, the top of the Oceanwatch tower, from where any approaching sails were visible first.

When the news of the Kalpan mission disaster were first briefly reported through the signaling towers from Darbash, Ambassador Tam immediately sought her audience. The audience was granted and lasted exactly fifteen seconds during which Her Majesty barely holding back her rage and in the voice that could freeze the sunlight ordered the Ambassador to collect as much information about the incident as possible and wait to be invited to give an explanation when all of the Ezeek mission members return home safely. Without being permitted to say a word, the Ambassador was then dismissed.

Depending on the prevailing winds, it would take three to five days for the ships to return. So Alice forced herself to conduct some government duties in the meanwhile. Two secretaries from the Administration Chamber sat opposite each other at the table and read the selected cases that required her attention.

\say{Petition for royal pardon,} announced one secretary while the other shuffled papers, \say{Kor Imlan, twenty-nine, decorated war veteran, killed two in a drunken bar fight, sentenced ten, served five, repentant, excellent behavior.}

\say{Granted,} murmured Alice.

\say{Complaint,} announced the other secretary, \say{Fishermen Guild of Port Rayton, too high local sales tax enforced by the municipality, citing ten percent above average, also granted the Temple permanent buy-out privilege for half a market price. Thirty percent fishing companies went bankrupt since the season begins, all sold allegedly to magistrate associates.}

\say{Refer to the Dark Eye, possible conspiracy between municipality and the Temple Priest, corruption charges, indecent market practices, probably monopolization.

Also, written commentary tomorrow from Bertha on why the hell does that shit needs to go all the way trhough me. Aren't there local Dark Eye office in Port Rayton?}

\say{Your Majesty, the Dark Eye personnel traditionally does not allow any official contacts with commoners if not undercover. Or anyone, for that matter. They are considered as\dots at your \textit{personal} disposal, not answerable to anyone else but the reigning monarch.}

\say{All right, I will see to it. Carry on.}

\say{Petition from Ezeek diaspora in Port Dauruna,} continued secretary and Alice shuddered, \say{Permission to build a monument to Uluna of the Enceris Dynasty, locally popular as\dots}

\say{I know who she was. What is the problem?}

\say{Municipality and Temple Priest are against installing it on the central square, arguing the diaspora has its own large city district.}

\say{Overruled, granted,} said Alice.

\say{Invitation from the Royal Academy of Arts and Sciences. Tricentennial anniversary of its foundation. Annual committee on Grants and Awards for gifted youngsters.}

\say{No, not this time.}

There was a knock in the door and the servant peered in, saying \say{Your Majesty, sails on approach from northwest, matching the "Dexterous".}

Alice nodded and dismissed both secretaries, saying \say{I will see the Special Envoy immediately.}

Unbearable minutes floated by. Door opened and Ferin stepped in with guilty look on his face. Alice stood and took a step towards him, thinking \say{don't run, don't run!} and ran. She crashed into him, hung on him, hugged him, punched him in the chest with her little fists, then hugged him again, all while crying and trying to say everything important at the same time.

At first second Ferin was in complete shock and did not know what to do but then his mating instincts finally kicked in to a full throttle. He hugged Alice, gently stroking and kissing her head and cheeks while wiping her endless waterfall of tears with his handkerchief and listening to horrible sobbing threats of curses she would inflict upon him should he "ever do that to her again". After a while, waterfall of tears mostly ceased, they sat quietly on a coach still hugging. They both did not know what to say but it seemed the words were not necessary.

Finally, Alice sobered up, regained self-confidence, stood and walked to her presiding chair, saying \say{Come on, Your Excellence, we have work to do.}

The Director of the Dark Eye, as is expected from the head of the secret police, was an average man with average face bearing no distinctive features whatsoever. Take your look away from him and you would not remember him at all.

\say{Director, please, begin with casualty report,} said Alice.

\say{Your Majesty,} replied Director, \say{of seventeen people assigned to the mission, four agents who were parts of a decoys, are alive and out of danger. Ten are confirmed dead as a result of an attack. Three more agents and the Lieutenant Niorn with four of his men are thought to have escaped the hotel but we are yet to contact and confirm their status. This makes the total number of casualties nineteen -- ten of ours and nine legionnaires.}

\say{Carry on,} encouraged Alice.

\say{The identity of the attackers can not yet be ascertained with enough degree of confidence. What we surely know is that they were not tribal raiders nor a municipal guardsmen nor an Ezeek armed forces. The working hypothesis is that it was either one of the criminal clan enforcers or some kind of private security team owned by the Dynastic Council or by some subgroup within it.

The attackers used two large carriages to block either entrance to the hotel, then a group of about thirty men stormed it through the balconies on the second floor. The second group of about ten attackers entered the fifth floor through the roof from neighboring buildings -- this was the group encountered by Lieutenant Niorn and his men when they, apparently, decided to escape the hotel via the roof. That second group is likely to have been destroyed although we are yet to hear any reports from Niorn or any of the men in his company. It should be noted that by now they already missed several deadlines and opportunities to make contact with our agents in Kalpan, which may indicate that they have been captured by the Council. Also, it is generally slow process since the closest signaling stations not under control of the Council are in Xubash which is several days ride from Kalpan. Even if they alive and free, we may not know it until much after, for example, if they decided to make it to Xubash rather than risk contacting and explosing the local ring.

The whole attack lasted eight minutes, and then the Wildfyre charge was detonated inside, per contingency plan. The hotel and two neighboring buildings burned out completely, and only the attackers who were outside at the moment of explosion, survived.}

\say{Official reactions? Rumors? Media coverage?} inquired Alice.

\say{Surprisingly scarce. The fire was reported as residential accident, no mention of any the attack on the diplomatic mission. So far the Dynastic Council has issued no relevant statements whatsoever. About the rumors,} Director hesitated, \say{Your Majesty, Ezeek people are far less curious and more busy with themselves than one might think. They are unlikely to spread rumors about the events that does not concern them personally or imminently. Such is their mentality.}

Alice once again put her legs on a table and considered the ornamented ceiling. She had hoped to reach some conclusion without involving Ambassador Tam but the general situation looked like they will need an insider information anyway. And, perhaps, once again base their analysis and decisions on the information provided by a man whose incentives had already cost Her Majesty many lives of her loyal subjects and whose good faith and peacemaking intentions remained dubious at best.

Alice rang a bell and called for Ambassador Tam.

\say{Meanwhile,} she said to Director of the Dark Eye, \say{Summarily, it looks like we know next to nothing for sure besides the basic timeline of events. And the spy ring in Kalpan is quote extensive, I take it? What do they do, I wonder?}

\say{Your Majesty,} replied the Director with light undertones of tiredness in his voice, \say{our persistently major problem with Kalpan and Ezeek in general is that most of our agents there are commoners. This is why our mission was so luckily forewarned -- someone closer to the circles of, say, private security services or "thugs-for-hire" as they are known locally, overheard certain calls and exchanges mentioning certain places and personalities with payouts promised being atypically higher than normal.

You see, in the Dark Domain the upwards social mobility exists such that, in theory, any peasant can reach almost any administrative position in the government solely on his or her merits and skills. But in the Nation of Ezeek the strategic decisions are made by nobles only. And it is extremely hard to infiltrate the Ezeek nobility due to the central role of dynasties in ther life.

A complete outsider with impenetrable legend can only join the dynasty as a family member, i.e. via marriage or adoption. But that does not grant them any of the dynastic privileges. They can not even style themselves as inlaws of dynastic head or Prince; they can participate in the tribal assembly but have no vote rights there. Only their children born in the union with the member of the Dynasty are considered full members with all the eligibilities this entails, but even then, line of Princely succession can be altered in favor of the younger heir if his bloodline joined the dynasty earlier than that of the older one.

Similarly it is hard to recruit an agent from a native nobility, for the same reason. Their loyalties to their Dynasties far exceed even their loyalty towards the Sceptre. The wielder of the Sceptre is not an absolute monarch but rather an "agreed upon" figure equally tolerable by all Princes, even though he has tangible authority over them. It takes an extraordinary circumstances for a member of the Dynasty, even not currently one with the elected Prince, to shift his or her loyalty elsewhere, risk expulsion and accept our offer even of being just an information source, not to mention more active roles.}

\say{Uh-huh,} said Alice, \say{So, I take it, of thirteen dynasties whose representatives were at the Council that day, we have informants in\dots none of them?}

\say{Unfortunately, Your Majesty, this is correct. You should understand that in the pre-war period we mostly focused on the Princely dynasties since they were responsible for military strategy and planning and most key decisions on Ezeek society. But their power structure since then, embodied by the Dynastic Council is far less transparent than ever before. We really know very little of it besides publicly available information and some peasant rumors.

Our analysts work day and night on the current members of the Council but the only discrepancy we have found so far is that most of them come from the top-management of major financial institutions -- bankers and suchlike. This is rather strange composition for the ruling body assembled allegedly to appoint the supreme leader of the nation.}

\say{Ambassador Tam and Councilor Kercak!} loudly announced the servant by the door.

The door opened and Ambassador Tam stepped in, followed by young man Ferin immediately recognized as the Dynastic Council member who made venomous remarks about his supposed citizenship. What the hell?

\say{Your Majesty!} voiced Ambassador as the duo bowed deeply and synchronously, \say{Let me again extend my deepest apologies about the unfortunate events that occured in Kalpan a few days ago. It is also very pleasing to see His Excellence Special Envoy Ferin alive and well. As per your request, Your Majesty, I had found an adequate means to explain the situation to our mutual benefit. This gifted boy is none other than Councilor Kercak, currently a member of the Ezeek Dynastic Council, who took the situation seriously enough to make it here personally, on his own volition, and, I dare say, against the will of the Interim President Emran and many his colleagues.}

Alice waved her hand, inviting the guests to sit and said \say{I am all ears.}

\say{Your Majesty,} began Kercak, \say{I must begin my discourse from the subject a bit farther from the unfortunate events in Kalpan, as the primary and innermost causes of them lie in the very core distinction between societal structures of the Nation of Ezeek and the Dark Domain.

People unfamiliar with the ways of Ezeek often judge us by the standards they themselves live by and that is the source of great many misunderstandings. For example, in the Dark Domain, Eternal Kingdom and many other countries on the continent the nature of nobility is defined by inheritance and wealth, but by the former to much less degree than by the latter. The nobility status is usually achieved as a result of owning the assets and properties that generate income. Passing the ownership down the generations ensures the inheritance of the nobility status. Bankrupt nobility risk losing its privileges eventually. Therefore the social stratification is very vague and dynamic, despite many great noble houses counting centuries of their recorded history.

On the contrary, nobility of the Nation of Ezeek are considered more as a keepers of the national traditions, ancestral faith and historical knowledge. Being tribal Prince, even the Sceptre wielder, was never about wealth and his inheritance is limited by the tribal representative procedures written in the Dynastic Codex. The Prince, in essence, is more of a spiritual position even though he traditionally holds much of administrative authority too.

Having said that, I wish to express my deepest sympaties towards Your Excellence Special Envoy for the position you voiced before the Council. Nowadays it is very rare opportunity to meet an Ezeek tribesmen with such deep and innate knowledge of our ancestral ways and laws. I am sorry if my remarks that day were a bit bitter -- I had to play my role, please, take no offense.}

\say{None taken, Kercak,} said Ferin, \say{but how exactly all these subtleties matter in the problem considered here?}

\say{Directly,} replied Kercak with very sad voice, \say{and I am ashamed that my Nation have come to such magnitude of disgrace. Look, my point is that all the accusations you made before the Council are all valid and true. Within the context of the Dynastic Codex we all are, indeed, criminals and usurpers. But there is no higher authority than the Dynastic Council. For the absence of Sceptre wielder, no one can force the Council back into the constraints of law. Sad, but true fact, that this Council is corrupted. You call them criminals, and they say nothing but they know that they are criminals indeed, only they do not care about that and about whatever you say since they know there is no one to judge them. I personally much appreciate your stance and efforts to point out what they are guilty of, but, you really should not expect more than "Yes, so what? Piss off!" in return.

It is very hard for me to find the proper words to describe the situation\dots Such is the magnitude of unthinkable!}

\say{Wait,} Alice interrupted skeptically, \say{this sounds almost too pathetic. Is entire Council corrupt that way? Or are we to believe that you are the only one with remaining sense of honor, dignity and adherence to the Ezeek traditions? Anyway, why do they do it? And, more importantly, you say you have to play your role, but it looks more like being complicit, actually. Why don't you step down in protest?}

\say{Your Majesty, I am not alone in my disdain, but my dynasty had entrusted me in this duty so I must endure. As to why they do it, the financial aid programs organized by Eternal Kingdom largely goes through banks owned by Emran and his co-conspirators and a network of their subsidiaries. They essentially own all of the Nation's economy and financial system and use it mostly for their own benefit.}

Alice glanced at Ferin, smiling as if reminding him of his escapade towards General Nhusen. Ferin noticed this and gritted his teeth.

\say{Well, then, explain the situation to your dynasty, call for tribal assembly or whatever. Expose and expulse the corrupted members and make the Council valid and legitimate. What is the problem?} asked Alice.

Kercak and Ferin exchanged quick glances towards each other and lowered their eyes in embarrassment. Kercak sighed deeply and did not answer. Ferin cleared his throat and said

\say{Let me guess. Majority of the Dynastic Council is corrupted, including Interim President Emran. Those dynasties who publicly voiced opposition to this state of things were expelled from the Council, this is why it is short of sixteen members. Those who remained but not included in the Emran schemes directly, quenched their guilt by a bit of gold. And here I came, naive idealistic idiot, and tried to teach them the ways of Ezeek. Am I right so far?}

\say{Yes, Your Excellence,} almost whispered Kercak, \say{they promised to include our dynasty into future concessions with Eternal Kingdom. It was either that or our tribe will be out begging on the streets. You know the situation, don't you? We had two hundred fishing boats prior to the war, now we have fifteen. Not hundreds, just fifteen. For the entire tribe. And no more merchant traffic from the southeast.}

\say{Merchant traffic, my ass.} intervened Alice, \say{You did mean raiders, didn't you?}

\say{Even animals hunt and kill to survive! Do you blame them for it?}, Kercak resented.

\say{This is rather excellent analogy, brother}, noticed Ferin gloomily, \say{you do indeed behave like animals and it would take decades of hard work to teach you the ways mankind learned to cooperate to mutual benefit, before you at least stop being proud of your old ways. I bet Emran had ordered us murdered right after I left the Council, had he not? Old fart.}

\say{I tipped off your agent about the impending attack,} said Kercak plainly. Director of the Dark Eye, who was taking notes, quickly glanced at him in surprise but said nothing.

\say{Thank you for that, Councilor. If it is true, of course,} remarked Alice.

\say{Everything I said here is true, Your Majesty,} said Kercak.

\say{I hope so,} mused Alice, {although, frankly, this is the second time I hear such honest sounding assurances from Ambassador Tam or someone associated with him. The first time I took it for truth had cost me dearly, the lives of several of my most loyal subjects were lost\dots}

\say{Your Majesty, I protest!} said Ambassador Tam loudly, \say{you don't seriously believe I could have knowingly put the embassy of the Dark Domain in mortal danger? The wicked ways of President Emran and his murderous intent were beyond my wildest imagination and possible foresight!}

\say{You don't get to protest, Ambassador}, replied Alice with hardened tone, \say{But something in your vision of the situation is way off the reality. You had promised me no less than popular revolt in Ezeek supported by the nobility supposedly severely disappointed in the Dynastic Council impotence. You said they were ready to oust it entirely.}

Kercak turned to Ambassador Tam with surprising look on his face. Uh-oh, thought Alice, someone's diplomatic career is about to experience drastic changes, unless he has equal or greater leverage on Kercak. Which is likely.

\say{I did not promise any of that, Your Majesty,} retorted Tam, \say{since none of it is under any kind of my control. It was simply my analysis of the situation. And it turned out I was wrong. I am not above human errors.}

\say{Whatever. What actually happened is that Interim President simply bought them all wholesale}, continued Alice, \say{and the peasantry simply did not care}.

\say{How could I know that? Nor Emran nor the Council do not report to me about their internal policies or even the proceedings of the Council,} reasoned Ambassador Tam.

Alice looked at him carefully for a few moments and then said

\say{It has been \textit{five years} since Dynastic Council was established and Interim President Emran assumed power. During that five years, the role of ruling nobility in Ezeek had apparently shifted from authoritative keepers of tradition to petty oligarchs interested only in accumulating personal wealth, disregarding some of the core Laws. This is rather drastic change for such a short period, don't you think? I mean, not something an experienced politician should simply dismiss.

My point is, either you did truly miss it, in which case you are an incompetent gullible fool or you did not miss it but had knowingly misinformed me and my embassy about the true nature of the Council and the aforementioned pivotal shift in what is considered acceptable and appropriate for Ezeek nobility nowadays. In which case you are an accomplice and, well, you had won this round, I admit.

But, mind you, Ambassador, this is a game I can stop and revert at any moment. While you, unfortunately, can not. Dismissed.}

Alice watched as the two departed her office, then turned towards the Director of the Dark Eye and said

\say{So, bankers, huh?}

\say{Yes, Your Majesty, this explains some of the unknown variables. Not all though. The Ambassador knows much more but not telling it.}

% Who handles the corruption?

\section{Observations}

Later that evening it was raining and Ferin was readying himself for sleep and sat on his bed flipping through his huge "Royal Encyclopedia of Ezeek" and through recent special issue of Ezeek newspaper dedicated to Fertility Games -- huge nationwide sporting event. The newspaper contained numerous schedules, charts and diagrams, detailing each sportsman or team per each discipline. This was the only event in Ezeek society where nobility and peasantry competed on equal grounds and where only your skill mattered.

Ferin's particular concern was the dynasties of each tribe, how numerous they were and who had produced Princes on tribal assemblies in the years prior to Great Winter War, and whether they lived to be represented on current Fertility Games. He was not sure what exactly worried him, but the recent days had inflicted on him so much of rethinking and reconsidering of things always thought to be immutable, so he decided to scan for possible clues in his favorite volume.

As he flipped through Encyclopedia, sometimes peeking into the newspaper for the relevant information, the more his yet non-verbal suspicion grew. Something was very wrong here.

\say{Tribe of Anok,} he murmured to himself, \say{six noble dynasties pre-war. Prince Lodos of Arcon dynasty. Now,} he shifted his look to the newspaper, \say{famous archers. Archery, fifty laces, dynasties Arif, Embet, Kutan, Yolan, Breber. Mounted archery, obstacle course, stationary targets, dynasties Arif, Kutan, Breber. No Arcon?}

This might have been a coincidence. But the Royal Encyclopedia listed Prince Wiltor of Chebet dynasty of Irtan tribe. And no entrant from Chebet into Games. And Prince Kalud of Hlud dynasty of Gevan tribe. No entrant from Hlud into Games.

Chill of dread ran down Ferin's spine. His heart started pounding rapidly. He remembered reprimanding the Dynastic Council of their supposed inability to find the surviving members of his and other Prince's dynasties. All in all, it was about three hundred people. In various places at various times, most of them never even met each other outside their own dynasty, and\dots Were they \textit{all} gone? How could it be?

Ferin startled as there were gentle knock on the door and then door opened and Alice wearing raincoat slipped in. As she walked towards him, Ferin began to say

\say{Oh, hi! Listen, I've found this\dots}

But her fingers covered his mouth, silencing him.

\say{Ferin,} said Alice menacingly, \say{enough of this shit for today. I've been deciding on the monument for your auntie, listened for not one but two lectures on functioning of the the society, witnessed the huge cultural shift and, quite possibly, once again found myself in conspiracy with foreign powers. You were so worried about my depersonalization, remember? So make it personal right now.}

She touched the lamp, putting it off, and in a smooth and swift motion dropped the raincoat down. It turned out to be the only clothing she wore.

And there was night and the night was dark and full of love.