\chapter{Additional material}

\section{The climate theory}

About two thirds of Ezeek territory lies in the rocky highlands and are unable to support steady subsistence farming, let alone sustainable cattle husbandry. Also, the Ezeek sea remains frozen well into late spring at these latitudes so navigation can not be opened until then. No trade destinations lie either to the north or west of major Ezeek ports. Combined with the fact that fish production volumes also suffer from the annual climate variations, it is quite expected that total food supply varies annually as well.

Let me put it in simpler terms. Every four to five years the ice layer covering the Shallow Strait between northern ocean and Ezeek sea grows so thick it remains unbroken well into mid-summer, and when it finally breaks, the sea and air temperature are already high enough that the icebergs melt completely long before they reach the latitudes of Kalpan valley. The high salinity in the upper sea layers thus prevents most species of fish from entering the major valley rivers upstream for spawning so they turn back and spawn in the rivers to the south of High Peaks. As a result -- no fish for poor Ezeek fishermen.

For the very same reason the northward warmwater circulation current does not restart at summer until, at least, Shallow Strait pack ice is broken and massive cold saltwater inflow from northern ocean displace the deep layers of the much warmer current at the southern Ezeek sea, pushing them closer to the surface. Until that happens, the temperature of the current does not rise, evaporation decreases and the eastward winds blowing from the sea over Kalpan valley and much of Ezeek inland territory do not carry enough moisture to precipitate. The germination of crops is delayed by at least two months and they can not ripe before northern winds start blowing over again. And even if the winds are seasonally delayed, the lack of moisture causes drought and you can not save your harvest by irrigation because that would entail the use of already seriously depleted Kalpan river system. What is worse in this situation is that even if salinity levels make Kalpan rivers accessible, You have to make a choice -- either let fish spawn in the valley in early spring and let your harvest die later or save the harvest but block the fish from spawning there when it had a chance.

Bear in mind, my dear boy, that this is very simplified explanation as we are still far away from knowing the works of nature in such a minute detail. Sometimes fish do manage to spawn in the Kalpan valley but the rains are still mostly absent, sometimes the opposite happens. It largely does not matter.

